---
title: "Coordination Success, Models, Correlations, Plots"
author: "MScStudent"
date: "20/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## read in data (for the generation of the data collection file, see the frist script)
```{r}
#read in combined German and English data with AS
alldata <- read.csv('alldatawithAS_E&G.csv', sep=",",
                    header=TRUE, 
                    na.strings=c("NA","na"), 
                    stringsAsFactors = TRUE) #unlemmatized

#alldata_lemma <- read.csv('lemmatized_alldata.csv', sep=",", #lemmatized  
                   # header=TRUE, 
                   # na.strings=c("NA","na"), 
                   # stringsAsFactors = TRUE) 

#unlemmatized version for the reasons explained in the thesis
```


```{r suppressPackageStartupMessages}
## Load packages

suppressPackageStartupMessages(library(data.table))
suppressPackageStartupMessages(library(stats))
suppressPackageStartupMessages(library(lme4))
suppressPackageStartupMessages(library(glmmTMB))
suppressPackageStartupMessages(library(MuMIn))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(boot))
suppressPackageStartupMessages(library(Rmisc))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(pander))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(magrittr))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(AER))
suppressPackageStartupMessages(library(r2glmm))
suppressPackageStartupMessages(library(ggthemes))
suppressPackageStartupMessages(library(ggpubr))
```



#get Coordination Success Scores (correctness scores)
#by-item for each try and each camera condition
(face cond (camera signaller=on))

#first try
```{r}

coordination_score_vector_face <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'face'),]
cues <- unique(group.data$first_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$first_cue == current_cue))
  number_of_successes <- length(which((group.data$first_cue == current_cue) & (group.data$numberoftries == 1)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue))))
coordination_score_vector_face <- append(coordination_score_vector_face, coordination_score)
}
names(coordination_score_vector_face) <- target_vector
coordination_score_vector_face



#by item (=target) for non-face condition, 1st try

coordination_score_vector_nonface <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'non-face'),]
cues <- unique(group.data$first_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$first_cue == current_cue))
  number_of_successes <- length(which((group.data$first_cue == current_cue) & (group.data$numberoftries == 1)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue)))) #first divided by nb signallers prod each of the signals, #then divided by nb guessers correctly guessing the item given each of the signals/nb guessers correctly guessing the target given each of the signals
coordination_score_vector_nonface <- append(coordination_score_vector_nonface, coordination_score) 
}
names(coordination_score_vector_nonface) <- target_vector
coordination_score_vector_nonface #40
```

#second try
```{r}
#by-item, face cond (camera signaller=on)

coordination_score_vector_face2 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'face'),]
cues <- unique(group.data$second_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$second_cue == current_cue))
  number_of_successes <- length(which((group.data$second_cue == current_cue) & (group.data$numberoftries == 2)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue)))) #still first cue bc if na, then non-valid trial
coordination_score_vector_face2 <- append(coordination_score_vector_face2, coordination_score)
}
names(coordination_score_vector_face2) <- target_vector
coordination_score_vector_face2

#by item (=target) for non-face condition

coordination_score_vector_nonface2 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'non-face'),]
cues <- unique(group.data$second_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$second_cue == current_cue))
  number_of_successes <- length(which((group.data$second_cue == current_cue) & (group.data$numberoftries == 2)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue))))
coordination_score_vector_nonface2 <- append(coordination_score_vector_nonface2, coordination_score)
}
names(coordination_score_vector_nonface2) <- target_vector
coordination_score_vector_nonface2

```


#third try
```{r}
#by-item, face cond (camera signaller=on)

coordination_score_vector_face3 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'face'),]
cues <- unique(group.data$third_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$third_cue == current_cue))
  number_of_successes <- length(which((group.data$third_cue == current_cue) & (group.data$numberoftries == 3)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue)))) #still first cue bc if na, then non-valid trial
coordination_score_vector_face3 <- append(coordination_score_vector_face3, coordination_score)
}
names(coordination_score_vector_face3) <- target_vector
coordination_score_vector_face3

#by item (=target) for non-face condition

coordination_score_vector_nonface3 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'non-face'),]
cues <- unique(group.data$third_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$third_cue == current_cue))
  number_of_successes <- length(which((group.data$third_cue == current_cue) & (group.data$numberoftries == 3)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue))))
coordination_score_vector_nonface3 <- append(coordination_score_vector_nonface3, coordination_score)
}
names(coordination_score_vector_nonface3) <- target_vector
coordination_score_vector_nonface3
```


#fourth try
```{r}
#by-item, face cond (camera signaller=on)

coordination_score_vector_face4 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'face'),]
cues <- unique(group.data$fourth_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$fourth_cue == current_cue))
  number_of_successes <- length(which((group.data$fourth_cue == current_cue) & (group.data$numberoftries == 4)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue)))) #still first cue bc if na, then non-valid trial
coordination_score_vector_face4 <- append(coordination_score_vector_face4, coordination_score)
}
names(coordination_score_vector_face4) <- target_vector
coordination_score_vector_face4

#by item (=target) for non-face condition

coordination_score_vector_nonface4 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'non-face'),]
cues <- unique(group.data$fourth_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$fourth_cue == current_cue))
  number_of_successes <- length(which((group.data$fourth_cue == current_cue) & (group.data$numberoftries == 4)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue))))
coordination_score_vector_nonface4 <- append(coordination_score_vector_nonface4, coordination_score)
}
names(coordination_score_vector_nonface4) <- target_vector
coordination_score_vector_nonface4
```


#fifth/final try

```{r}
#by-item, face cond (camera signaller=on)

coordination_score_vector_face5 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'face'),]
cues <- unique(group.data$fifth_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$fifth_cue == current_cue))
  number_of_successes <- length(which((group.data$fifth_cue == current_cue) & (group.data$numberoftries == 5)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue)))) #still first cue bc if na, then non-valid trial
coordination_score_vector_face5 <- append(coordination_score_vector_face5, coordination_score)
}
names(coordination_score_vector_face5) <- target_vector
coordination_score_vector_face5

#by item (=target) for non-face condition

coordination_score_vector_nonface5 <-c()
target_vector <- unique(alldata$target)
for (i in (1:length(target_vector))){ 
current_target <- target_vector[i]
group.data <- alldata[which(alldata$target == current_target & alldata$condition == 'non-face'),]
cues <- unique(group.data$fifth_cue)
cue_vector <- c()
occurrences_vector <- c()
success_vector <- c()
for (inner_index in (1:length(cues))){
  current_cue <- as.character(cues[inner_index])
  occurrences <- length(which(group.data$fifth_cue == current_cue))
  number_of_successes <- length(which((group.data$fifth_cue == current_cue) & (group.data$numberoftries == 5)))
  cue_vector <- append(cue_vector, current_cue)
  occurrences_vector <- append(occurrences_vector, occurrences)
  success_vector <- append(success_vector, number_of_successes)
}
coordination_score <- sum((occurrences_vector/length(!is.na(group.data$first_cue)))*(success_vector/length(!is.na(group.data$first_cue))))
coordination_score_vector_nonface5 <- append(coordination_score_vector_nonface5, coordination_score)
}
names(coordination_score_vector_nonface5) <- target_vector
coordination_score_vector_nonface5
```







#Plot first try
```{r}
#in ascending order
coordination_score_vector_nonface_sorted <- coordination_score_vector_nonface[order(coordination_score_vector_nonface, decreasing=FALSE)]
coordination_score_vector_face_sorted <- coordination_score_vector_face[names(coordination_score_vector_nonface_sorted)]

names_targets=as.character(names(coordination_score_vector_nonface_sorted))
names(names_targets) <- c(1:length(names_targets))
names_targets[25] <- "Brücke"
names_targets[35] <- "Rüstung"
data_ggplot1 <- data.frame(names_targets=c(names_targets, names_targets), condition=c(rep("non-face", length(names_targets)), rep("face", length(names_targets))), coordination_score=c(coordination_score_vector_nonface_sorted, coordination_score_vector_face_sorted))
data_ggplot1$names_targets <- factor(data_ggplot1$names_targets, levels=names_targets)
fig1 <- ggplot(data_ggplot1, aes(x=names_targets, y=coordination_score, color=condition)) +
  geom_point() + 
  theme_classic() + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  ylab("Coordination Success") + xlab("Target Items")
fig1
````

#plot 2nd try

```{r}
coordination_score_vector_nonface2_sorted <- coordination_score_vector_nonface2[order(coordination_score_vector_nonface2, decreasing=FALSE)]
coordination_score_vector_face2_sorted <- coordination_score_vector_face2[names(coordination_score_vector_nonface2_sorted)]

names_targets=as.character(names(coordination_score_vector_nonface2_sorted))
names(names_targets) <- c(1:length(names_targets))
names_targets[23] <- "Brücke"
names_targets[15] <- "Rüstung"
data_ggplot2 <- data.frame(names_targets=c(names_targets, names_targets), condition=c(rep("non-face", length(names_targets)), rep("face", length(names_targets))), coordination_score=c(coordination_score_vector_nonface2_sorted, coordination_score_vector_face2_sorted))
data_ggplot2$names_targets <- factor(data_ggplot2$names_targets, levels=names_targets)
fig2 <- ggplot(data_ggplot2, aes(x=names_targets, y=coordination_score, color=condition)) +
  geom_point(alpha=0.6) + 
  theme_classic() + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  ylab("Coordination Success") + xlab("Target Items")
fig2
```

#plot 3rd try
```{r}
coordination_score_vector_nonface3_sorted <- coordination_score_vector_nonface3[order(coordination_score_vector_nonface3, decreasing=FALSE)]
coordination_score_vector_face3_sorted <- coordination_score_vector_face3[names(coordination_score_vector_nonface3_sorted)]

names_targets=as.character(names(coordination_score_vector_nonface3_sorted))
names(names_targets) <- c(1:length(names_targets))
names_targets[25] <- "Brücke"
names_targets[35] <- "Rüstung"
data_ggplot3 <- data.frame(names_targets=c(names_targets, names_targets), condition=c(rep("non-face", length(names_targets)), rep("face", length(names_targets))), coordination_score=c(coordination_score_vector_nonface3_sorted, coordination_score_vector_face3_sorted))
data_ggplot3$names_targets <- factor(data_ggplot3$names_targets, levels=names_targets)
fig3 <- ggplot(data_ggplot3, aes(x=names_targets, y=coordination_score, color=condition)) +
  geom_point(alpha=0.6) + 
  theme_classic() + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  ylab("Coordination Success") + xlab("Target Items")
fig3

```



#plot 4th try
```{r}
#in ascending order
coordination_score_vector_nonface4_sorted <- coordination_score_vector_nonface4[order(coordination_score_vector_nonface4, decreasing=FALSE)]
coordination_score_vector_face4_sorted <- coordination_score_vector_face4[names(coordination_score_vector_nonface4_sorted)]

names_targets=as.character(names(coordination_score_vector_nonface4_sorted))
names(names_targets) <- c(1:length(names_targets))
names_targets[38] <- "Brücke"
names_targets[32] <- "Rüstung"
data_ggplot4 <- data.frame(names_targets=c(names_targets, names_targets), condition=c(rep("non-face", length(names_targets)), rep("face", length(names_targets))), coordination_score=c(coordination_score_vector_nonface4_sorted, coordination_score_vector_face4_sorted))
data_ggplot4$names_targets <- factor(data_ggplot4$names_targets, levels=names_targets)
fig4 <- ggplot(data_ggplot4, aes(x=names_targets, y=coordination_score, color=condition)) +
  geom_point(alpha=0.6) + 
  theme_classic() + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  ylab("Coordination Success") + xlab("Target Items")
fig4

```



#Plot fifth try
```{r}
coordination_score_vector_nonface5_sorted <- coordination_score_vector_nonface5[order(coordination_score_vector_nonface5, decreasing=FALSE)]
coordination_score_vector_face5_sorted <- coordination_score_vector_face5[names(coordination_score_vector_nonface5_sorted)]

names_targets=as.character(names(coordination_score_vector_nonface5_sorted))
names(names_targets) <- c(1:length(names_targets))
names_targets[39] <- "Brücke"
names_targets[33] <- "Rüstung"
data_ggplot5 <- data.frame(names_targets=c(names_targets, names_targets), condition=c(rep("non-face", length(names_targets)), rep("face", length(names_targets))), coordination_score=c(coordination_score_vector_nonface5_sorted, coordination_score_vector_face5_sorted))
data_ggplot5$names_targets <- factor(data_ggplot5$names_targets, levels=names_targets)
fig5 <- ggplot(data_ggplot5, aes(x=names_targets, y=coordination_score, color=condition)) +
  geom_point(alpha=0.6) + 
  theme_classic() + 
  scale_x_discrete(guide = guide_axis(angle = 90)) + 
  ylab("Coordination Success") + xlab("Target Items")
fig5

```




*By Pair Correctness Scores for each camera condition*
```{r}
#face
pair_score_vector_face_pair <-c()
pair_vector <- unique(alldata$pair)
for (i in (1:length(pair_vector))){ 
current_pair <- pair_vector[i]
group.data <- alldata[which(alldata$pair == current_pair & alldata$condition == 'face'),]
number_of_targets_guessed_in_all_turns <- length(unique(group.data$target))
print(number_of_targets_guessed_in_all_turns)#sanity check #always 20 bc all guessed by fifth cue
print(as.numeric(group.data$numberoftries)) #sanity check
pair_score <- number_of_targets_guessed_in_all_turns/sum(group.data$numberoftries, na.rm = TRUE)
pair_score_vector_face_pair <- append(pair_score_vector_face_pair, pair_score)
}
names(pair_score_vector_face_pair) <- pair_vector
pair_score_vector_face_pair

na.omit(pair_score_vector_face_pair)

names_pairs <- names(pair_score_vector_face_pair)
names_pairs


#non-face

pair_score_vector_nonface_pair <-c()
pair_vector <- unique(alldata$pair)
for (i in (1:length(pair_vector))){ 
current_pair <- pair_vector[i]
group.data <- alldata[which(alldata$pair == current_pair & alldata$condition == 'non-face'),]
number_of_targets_guessed_in_all_turns <- length(unique(group.data$target))
print(number_of_targets_guessed_in_all_turns)#sanity check
print(group.data$numberoftries) #sanity check
pair_score <- number_of_targets_guessed_in_all_turns/sum(group.data$numberoftries, na.rm=TRUE)
pair_score_vector_nonface_pair <- append(pair_score_vector_nonface_pair, pair_score)
}
names(pair_score_vector_nonface_pair) <- pair_vector
pair_score_vector_nonface_pair
```


#By-pair plots
*in ascending order*
```{r}
pair_score_vector_face_pair_without_NaN <- pair_score_vector_face_pair[which(!is.na(pair_score_vector_face_pair))]
pair_score_vector_face_pair_without_NaN_sorted <- pair_score_vector_face_pair_without_NaN[order(pair_score_vector_face_pair_without_NaN, decreasing = FALSE)]

pair_score_vector_nonface_pair_without_NaN <- pair_score_vector_nonface_pair[which(!is.na(pair_score_vector_nonface_pair))]
pair_score_vector_nonface_pair_without_NaN_sorted <- pair_score_vector_nonface_pair_without_NaN[order(pair_score_vector_nonface_pair_without_NaN, decreasing = FALSE)]
png(filename="pairlinear.png")
fig_face <- plot_ly(type='scatter') #(type='scatter')

fig_face <- fig_face %>% add_trace(x=1:length(pair_score_vector_face_pair_without_NaN_sorted), y = pair_score_vector_face_pair_without_NaN_sorted, name = "face", marker=list(color='salmon', size=7, line = list(color = 'black', width = 1.0)), na.omit)

fig_face <- fig_face %>% add_trace(x=c(1:length(pair_score_vector_nonface_pair_without_NaN_sorted))+length(pair_score_vector_face_pair_without_NaN_sorted), y = pair_score_vector_nonface_pair_without_NaN_sorted, name = "non-face", marker=list(color='mediumblue', size=7, line = list(color = 'black', width = 1.0)), na.omit)

fig_face <- fig_face %>% add_trace(x=length(pair_score_vector_face_pair_without_NaN_sorted)/2 , type='box', y = pair_score_vector_face_pair_without_NaN_sorted, name = NULL, marker=list(color='salmon', opacity = 0), na.omit, showlegend = F)

fig_face <- fig_face %>% add_trace(x=length(pair_score_vector_face_pair_without_NaN_sorted)+(length(pair_score_vector_nonface_pair_without_NaN_sorted)/2) , type='box', y = pair_score_vector_nonface_pair_without_NaN_sorted, name = NULL, marker=list(color='mediumblue', opacity = 0), na.omit, showlegend = F)

fig_face <- fig_face %>% layout(xaxis = list(title = "Pairs by Camera Condition",  showgrid=F,zeroline=F,showline=T, showticklabels=F),#, ),    
      yaxis = list(title = "Coordination Success", showline=T, showgrid=F, range=(c(0.3,1)), showticks=T, showticklabels = TRUE)) 


fig_face #screenshot! in plotly

```

*clouds (participation order)*
```{r}
fig_face <- plot_ly(type='scatter') #(type='scatter')
fig_face <- fig_face %>% add_trace(x=1:28, y = pair_score_vector_face_pair, name = "face", marker=list(color='salmon'), na.omit)
fig_face <- fig_face %>% add_trace(x=30:57, y = pair_score_vector_nonface_pair, name = "non-face", marker=list(color='mediumblue'), na.omit)

fig_face <- fig_face %>% layout(xaxis = list(title = "Pairs by Camera Condition",  showgrid=F,zeroline=F,showline=T, showticklabels=F),#, ),    
      yaxis = list(title = "Coordination Success", showline=T, showgrid=F, range=(c(0.3,1)), showticks=T, showticklabels = TRUE)) 
  
fig_face
```

*by pair language plot*

```{r}
# German
pair_score_vector_german_pair <-c()
pair_vector <- unique(alldata$pair[which(alldata$language=="German")])
for (i in (1:length(pair_vector))){ 
current_pair <- pair_vector[i]
group.data <- alldata[which(alldata$pair == current_pair),]
number_of_targets_guessed_in_all_turns <- length(unique(group.data$target))
print(number_of_targets_guessed_in_all_turns)#sanity check
print(group.data$numberoftries) #sanity check
pair_score <- number_of_targets_guessed_in_all_turns/sum(group.data$numberoftries, na.rm=TRUE)
pair_score_vector_german_pair <- append(pair_score_vector_german_pair, pair_score)
}
names(pair_score_vector_german_pair) <- pair_vector
pair_score_vector_german_pair


# English
pair_score_vector_english_pair <-c()
pair_vector <- unique(alldata$pair[which(alldata$language=="English")])
for (i in (1:length(pair_vector))){ 
current_pair <- pair_vector[i]
group.data <- alldata[which(alldata$pair == current_pair),]
number_of_targets_guessed_in_all_turns <- length(unique(group.data$target))
print(number_of_targets_guessed_in_all_turns)#sanity check
print(group.data$numberoftries) #sanity check
pair_score <- number_of_targets_guessed_in_all_turns/sum(group.data$numberoftries, na.rm=TRUE)
pair_score_vector_english_pair <- append(pair_score_vector_english_pair, pair_score)
}
names(pair_score_vector_english_pair) <- pair_vector
pair_score_vector_english_pair

```



#Preparation: to get BAS by item for the by-item BAS and by-item coordination success correlation
*start with Engl*

```{r}
#alldata_F$bas_tcfirst<-as.numeric(alldata_F$bas_tcfirst)

#delete whitespace
#alldata$target<-gsub(" ", "", alldata$target, fixed = TRUE)

alldata_F<-alldata %>% filter(condition=='face')


#FACE
#bulb 
bulb1_face <- alldata_F[which(as.character(alldata_F$target) == "bulb"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bulb")] <- bulb1_face
bulb1_face

bulb2_face <- alldata_F[which(as.character(alldata_F$target) == "bulb"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bulb")] <- bulb2_face
bulb2_face

bulb3_face <- alldata_F[which(as.character(alldata_F$target) == "bulb"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bulb")] <- bulb3_face
bulb3_face

bulb4_face <- alldata_F[which(as.character(alldata_F$target) == "bulb"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bulb")] <- bulb4_face
bulb4_face

bulb5_face <- alldata_F[which(as.character(alldata_F$target) == "bulb"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bulb")] <- bulb5_face
bulb5_face


#FACE
#bank 
bank1_face <- alldata_F[which(as.character(alldata_F$target) == "bank"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bank")] <- bank1_face
bank1_face

bank2_face <- alldata_F[which(as.character(alldata_F$target) == "bank"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bank")] <- bank2_face
bank2_face

bank3_face <- alldata_F[which(as.character(alldata_F$target) == "bank"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bank")] <- bank3_face
bank3_face

bank4_face <- alldata_F[which(as.character(alldata_F$target) == "bank"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bank")] <- bank4_face
bank4_face

bank5_face <- alldata_F[which(as.character(alldata_F$target) == "bank"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bank")] <- bank5_face
bank5_face

#FACE
#brewery 
brewery1_face <- alldata_F[which(as.character(alldata_F$target) == "brewery"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "brewery")] <- brewery1_face
brewery1_face

brewery2_face <- alldata_F[which(as.character(alldata_F$target) == "brewery"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "brewery")] <- brewery2_face
brewery2_face

brewery3_face <- alldata_F[which(as.character(alldata_F$target) == "brewery"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "brewery")] <- brewery3_face
brewery3_face

brewery4_face <- alldata_F[which(as.character(alldata_F$target) == "brewery"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "brewery")] <- brewery4_face
brewery4_face

brewery5_face <- alldata_F[which(as.character(alldata_F$target) == "brewery"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "brewery")] <- brewery5_face
brewery5_face



#FACE
#crescent 
crescent1_face <- alldata_F[which(as.character(alldata_F$target) == "crescent"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crescent")] <- crescent1_face
crescent1_face

crescent2_face <- alldata_F[which(as.character(alldata_F$target) == "crescent"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crescent")] <- crescent2_face
crescent2_face

crescent3_face <- alldata_F[which(as.character(alldata_F$target) == "crescent"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crescent")] <- crescent3_face
crescent3_face

crescent4_face <- alldata_F[which(as.character(alldata_F$target) == "crescent"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crescent")] <- crescent4_face
crescent4_face

crescent5_face <- alldata_F[which(as.character(alldata_F$target) == "crescent"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crescent")] <- crescent5_face
crescent5_face


#FACE
#affection 
affection1_face <- alldata_F[which(as.character(alldata_F$target) == "affection"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "affection")] <- affection1_face
affection1_face

affection2_face <- alldata_F[which(as.character(alldata_F$target) == "affection"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "affection")] <- affection2_face
affection2_face

affection3_face <- alldata_F[which(as.character(alldata_F$target) == "affection"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "affection")] <- affection3_face
affection3_face

affection4_face <- alldata_F[which(as.character(alldata_F$target) == "affection"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "affection")] <- affection4_face
affection4_face

affection5_face <- alldata_F[which(as.character(alldata_F$target) == "affection"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "affection")] <- affection5_face
affection5_face

#FACE
#sill 
sill1_face <- alldata_F[which(as.character(alldata_F$target) == "sill"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "sill")] <- sill1_face
sill1_face

sill2_face <- alldata_F[which(as.character(alldata_F$target) == "sill"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "sill")] <- sill2_face
sill2_face

sill3_face <- alldata_F[which(as.character(alldata_F$target) == "sill"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "sill")] <- sill3_face
sill3_face

sill4_face <- alldata_F[which(as.character(alldata_F$target) == "sill"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "sill")] <- sill4_face
sill4_face

sill5_face <- alldata_F[which(as.character(alldata_F$target) == "sill"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "sill")] <- sill5_face
sill5_face



#FACE
#yolk 
yolk1_face <- alldata_F[which(as.character(alldata_F$target) == "yolk"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "yolk")] <- yolk1_face
yolk1_face

yolk2_face <- alldata_F[which(as.character(alldata_F$target) == "yolk"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "yolk")] <- yolk2_face
yolk2_face

yolk3_face <- alldata_F[which(as.character(alldata_F$target) == "yolk"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "yolk")] <- yolk3_face
yolk3_face

yolk4_face <- alldata_F[which(as.character(alldata_F$target) == "yolk"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "yolk")] <- yolk4_face
yolk4_face

yolk5_face <- alldata_F[which(as.character(alldata_F$target) == "yolk"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "yolk")] <- yolk5_face
yolk5_face


#FACE
#loaf 
loaf1_face <- alldata_F[which(as.character(alldata_F$target) == "loaf"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "loaf")] <- loaf1_face
loaf1_face

loaf2_face <- alldata_F[which(as.character(alldata_F$target) == "loaf"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "loaf")] <- loaf2_face
loaf2_face

loaf3_face <- alldata_F[which(as.character(alldata_F$target) == "loaf"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "loaf")] <- loaf3_face
loaf3_face

loaf4_face <- alldata_F[which(as.character(alldata_F$target) == "loaf"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "loaf")] <- loaf4_face
loaf4_face

loaf5_face <- alldata_F[which(as.character(alldata_F$target) == "loaf"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "loaf")] <- loaf5_face
loaf5_face


#FACE
#cob 
cob1_face <- alldata_F[which(as.character(alldata_F$target) == "cob"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cob")] <- cob1_face
cob1_face

cob2_face <- alldata_F[which(as.character(alldata_F$target) == "cob"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cob")] <- cob2_face
cob2_face

cob3_face <- alldata_F[which(as.character(alldata_F$target) == "cob"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cob")] <- cob3_face
cob3_face

cob4_face <- alldata_F[which(as.character(alldata_F$target) == "cob"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cob")] <- cob4_face
cob4_face

cob5_face <- alldata_F[which(as.character(alldata_F$target) == "cob"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cob")] <- cob5_face
cob5_face


#FACE
#retina 
retina1_face <- alldata_F[which(as.character(alldata_F$target) == "retina"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "retina")] <- retina1_face
retina1_face

retina2_face <- alldata_F[which(as.character(alldata_F$target) == "retina"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "retina")] <- retina2_face
retina2_face

retina3_face <- alldata_F[which(as.character(alldata_F$target) == "retina"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "retina")] <- retina3_face
retina3_face

retina4_face <- alldata_F[which(as.character(alldata_F$target) == "retina"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "retina")] <- retina4_face
retina4_face

retina5_face <- alldata_F[which(as.character(alldata_F$target) == "retina"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "retina")] <- retina5_face
retina5_face


#FACE
#grater 
grater1_face <- alldata_F[which(as.character(alldata_F$target) == "grater"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "grater")] <- grater1_face
grater1_face

grater2_face <- alldata_F[which(as.character(alldata_F$target) == "grater"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "grater")] <- grater2_face
grater2_face

grater3_face <- alldata_F[which(as.character(alldata_F$target) == "grater"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "grater")] <- grater3_face
grater3_face

grater4_face <- alldata_F[which(as.character(alldata_F$target) == "grater"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "grater")] <- grater4_face
grater4_face

grater5_face <- alldata_F[which(as.character(alldata_F$target) == "grater"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "grater")] <- grater5_face
grater5_face


#FACE
#steed 
steed1_face <- alldata_F[which(as.character(alldata_F$target) == "steed"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "steed")] <- steed1_face
steed1_face

steed2_face <- alldata_F[which(as.character(alldata_F$target) == "steed"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "steed")] <- steed2_face
steed2_face

steed3_face <- alldata_F[which(as.character(alldata_F$target) == "steed"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "steed")] <- steed3_face
steed3_face

steed4_face <- alldata_F[which(as.character(alldata_F$target) == "steed"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "steed")] <- steed4_face
steed4_face

steed5_face <- alldata_F[which(as.character(alldata_F$target) == "steed"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "steed")] <- steed5_face
steed5_face

#FACE
#pepperoni 
pepperoni1_face <- alldata_F[which(as.character(alldata_F$target) == "pepperoni"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "pepperoni")] <- pepperoni1_face
pepperoni1_face

pepperoni2_face <- alldata_F[which(as.character(alldata_F$target) == "pepperoni"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "pepperoni")] <- pepperoni2_face
pepperoni2_face

pepperoni3_face <- alldata_F[which(as.character(alldata_F$target) == "pepperoni"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "pepperoni")] <- pepperoni3_face
pepperoni3_face

pepperoni4_face <- alldata_F[which(as.character(alldata_F$target) == "pepperoni"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "pepperoni")] <- pepperoni4_face
pepperoni4_face

pepperoni5_face <- alldata_F[which(as.character(alldata_F$target) == "pepperoni"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "pepperoni")] <- pepperoni5_face
pepperoni5_face


#FACE
#cod 
cod1_face <- alldata_F[which(as.character(alldata_F$target) == "cod"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cod")] <- cod1_face
cod1_face

cod2_face <- alldata_F[which(as.character(alldata_F$target) == "cod"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cod")] <- cod2_face
cod2_face

cod3_face <- alldata_F[which(as.character(alldata_F$target) == "cod"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cod")] <- cod3_face
cod3_face

cod4_face <- alldata_F[which(as.character(alldata_F$target) == "cod"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cod")] <- cod4_face
cod4_face

cod5_face <- alldata_F[which(as.character(alldata_F$target) == "cod"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "cod")] <- cod5_face
cod5_face



#FACE
#crossword 
crossword1_face <- alldata_F[which(as.character(alldata_F$target) == "crossword"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crossword")] <- crossword1_face
crossword1_face

crossword2_face <- alldata_F[which(as.character(alldata_F$target) == "crossword"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crossword")] <- crossword2_face
crossword2_face

crossword3_face <- alldata_F[which(as.character(alldata_F$target) == "crossword"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crossword")] <- crossword3_face
crossword3_face

crossword4_face <- alldata_F[which(as.character(alldata_F$target) == "crossword"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crossword")] <- crossword4_face
crossword4_face

crossword5_face <- alldata_F[which(as.character(alldata_F$target) == "crossword"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "crossword")] <- crossword5_face
crossword5_face


#FACE
#blaze 
blaze1_face <- alldata_F[which(as.character(alldata_F$target) == "blaze"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "blaze")] <- blaze1_face
blaze1_face

blaze2_face <- alldata_F[which(as.character(alldata_F$target) == "blaze"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "blaze")] <- blaze2_face
blaze2_face

blaze3_face <- alldata_F[which(as.character(alldata_F$target) == "blaze"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "blaze")] <- blaze3_face
blaze3_face

blaze4_face <- alldata_F[which(as.character(alldata_F$target) == "blaze"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "blaze")] <- blaze4_face
blaze4_face

blaze5_face <- alldata_F[which(as.character(alldata_F$target) == "blaze"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "blaze")] <- blaze5_face
blaze5_face

#FACE
#occupation

occupation1_face <- alldata_F[which(as.character(alldata_F$target) == "occupation"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "occupation")] <- occupation1_face
occupation1_face

occupation2_face <- alldata_F[which(as.character(alldata_F$target) == "occupation"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "occupation")] <- occupation2_face
occupation2_face

occupation3_face <- alldata_F[which(as.character(alldata_F$target) == "occupation"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "occupation")] <- occupation3_face
occupation3_face

occupation4_face <- alldata_F[which(as.character(alldata_F$target) == "occupation"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "occupation")] <- occupation4_face
occupation4_face

occupation5_face <- alldata_F[which(as.character(alldata_F$target) == "occupation"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "occupation")] <- occupation5_face
occupation5_face

#FACE
#butcher 
butcher1_face <- alldata_F[which(as.character(alldata_F$target) == "butcher"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "butcher")] <- butcher1_face
butcher1_face

butcher2_face <- alldata_F[which(as.character(alldata_F$target) == "butcher"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "butcher")] <- butcher2_face
butcher2_face

butcher3_face <- alldata_F[which(as.character(alldata_F$target) == "butcher"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "butcher")] <- butcher3_face
butcher3_face

butcher4_face <- alldata_F[which(as.character(alldata_F$target) == "butcher"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "butcher")] <- butcher4_face
butcher4_face

butcher5_face <- alldata_F[which(as.character(alldata_F$target) == "butcher"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "butcher")] <- butcher5_face
butcher5_face


#FACE
#bouquet 
bouquet1_face <- alldata_F[which(as.character(alldata_F$target) == "bouquet"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bouquet")] <- bouquet1_face
bouquet1_face

bouquet2_face <- alldata_F[which(as.character(alldata_F$target) == "bouquet"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bouquet")] <- bouquet2_face
bouquet2_face

bouquet3_face <- alldata_F[which(as.character(alldata_F$target) == "bouquet"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bouquet")] <- bouquet3_face
bouquet3_face

bouquet4_face <- alldata_F[which(as.character(alldata_F$target) == "bouquet"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bouquet")] <- bouquet4_face
bouquet4_face

bouquet5_face <- alldata_F[which(as.character(alldata_F$target) == "bouquet"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "bouquet")] <- bouquet5_face
bouquet5_face

#FACE
#acquaintance 
acquaintance1_face <- alldata_F[which(as.character(alldata_F$target) == "acquaintance"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "acquaintance")] <- acquaintance1_face
acquaintance1_face

acquaintance2_face <- alldata_F[which(as.character(alldata_F$target) == "acquaintance"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "acquaintance")] <- acquaintance2_face
acquaintance2_face

acquaintance3_face <- alldata_F[which(as.character(alldata_F$target) == "acquaintance"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "acquaintance")] <- acquaintance3_face
acquaintance3_face

acquaintance4_face <- alldata_F[which(as.character(alldata_F$target) == "acquaintance"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "acquaintance")] <- acquaintance4_face
acquaintance4_face

acquaintance5_face <- alldata_F[which(as.character(alldata_F$target) == "acquaintance"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "acquaintance")] <- acquaintance5_face
acquaintance5_face



#German FACE

alldata_F<-alldata_F %>% filter(condition=='face')
alldata_F

#FACE
#Krone 
Krone1_face <- alldata_F[which(as.character(alldata_F$target) == "Krone"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Krone")] <- Krone1_face
Krone1_face

Krone2_face <- alldata_F[which(as.character(alldata_F$target) == "Krone"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Krone")] <- Krone2_face
Krone2_face

Krone3_face <- alldata_F[which(as.character(alldata_F$target) == "Krone"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Krone")] <- Krone3_face
Krone3_face

Krone4_face <- alldata_F[which(as.character(alldata_F$target) == "Krone"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Krone")] <- Krone4_face
Krone4_face

Krone5_face <- alldata_F[which(as.character(alldata_F$target) == "Krone"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Krone")] <- Krone5_face
Krone5_face


#FACE
#Hafen 
Hafen1_face <- alldata_F[which(as.character(alldata_F$target) == "Hafen"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hafen")] <- Hafen1_face
Hafen1_face

Hafen2_face <- alldata_F[which(as.character(alldata_F$target) == "Hafen"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hafen")] <- Hafen2_face
Hafen2_face

Hafen3_face <- alldata_F[which(as.character(alldata_F$target) == "Hafen"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hafen")] <- Hafen3_face
Hafen3_face

Hafen4_face <- alldata_F[which(as.character(alldata_F$target) == "Hafen"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hafen")] <- Hafen4_face
Hafen4_face

Hafen5_face <- alldata_F[which(as.character(alldata_F$target) == "Hafen"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hafen")] <- Hafen5_face
Hafen5_face

#FACE
#Brunnen 
Brunnen1_face <- alldata_F[which(as.character(alldata_F$target) == "Brunnen"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brunnen")] <- Brunnen1_face
Brunnen1_face

Brunnen2_face <- alldata_F[which(as.character(alldata_F$target) == "Brunnen"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brunnen")] <- Brunnen2_face
Brunnen2_face

Brunnen3_face <- alldata_F[which(as.character(alldata_F$target) == "Brunnen"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brunnen")] <- Brunnen3_face
Brunnen3_face

Brunnen4_face <- alldata_F[which(as.character(alldata_F$target) == "Brunnen"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brunnen")] <- Brunnen4_face
Brunnen4_face

Brunnen5_face <- alldata_F[which(as.character(alldata_F$target) == "Brunnen"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brunnen")] <- Brunnen5_face
Brunnen5_face



#FACE
#Kamm 
Kamm1_face <- alldata_F[which(as.character(alldata_F$target) == "Kamm"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Kamm")] <- Kamm1_face
Kamm1_face

Kamm2_face <- alldata_F[which(as.character(alldata_F$target) == "Kamm"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Kamm")] <- Kamm2_face
Kamm2_face

Kamm3_face <- alldata_F[which(as.character(alldata_F$target) == "Kamm"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Kamm")] <- Kamm3_face
Kamm3_face

Kamm4_face <- alldata_F[which(as.character(alldata_F$target) == "Kamm"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Kamm")] <- Kamm4_face
Kamm4_face

Kamm5_face <- alldata_F[which(as.character(alldata_F$target) == "Kamm"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Kamm")] <- Kamm5_face
Kamm5_face


#FACE
#Dach 
Dach1_face <- alldata_F[which(as.character(alldata_F$target) == "Dach"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Dach")] <- Dach1_face
Dach1_face

Dach2_face <- alldata_F[which(as.character(alldata_F$target) == "Dach"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Dach")] <- Dach2_face
Dach2_face

Dach3_face <- alldata_F[which(as.character(alldata_F$target) == "Dach"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Dach")] <- Dach3_face
Dach3_face

Dach4_face <- alldata_F[which(as.character(alldata_F$target) == "Dach"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Dach")] <- Dach4_face
Dach4_face

Dach5_face <- alldata_F[which(as.character(alldata_F$target) == "Dach"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Dach")] <- Dach5_face
Dach5_face

#FACE
#Lilie 
Lilie1_face <- alldata_F[which(as.character(alldata_F$target) == "Lilie"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lilie")] <- Lilie1_face
Lilie1_face

Lilie2_face <- alldata_F[which(as.character(alldata_F$target) == "Lilie"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lilie")] <- Lilie2_face
Lilie2_face

Lilie3_face <- alldata_F[which(as.character(alldata_F$target) == "Lilie"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lilie")] <- Lilie3_face
Lilie3_face

Lilie4_face <- alldata_F[which(as.character(alldata_F$target) == "Lilie"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lilie")] <- Lilie4_face
Lilie4_face

Lilie5_face <- alldata_F[which(as.character(alldata_F$target) == "Lilie"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lilie")] <- Lilie5_face
Lilie5_face



#FACE
#Paddel 
Paddel1_face <- alldata_F[which(as.character(alldata_F$target) == "Paddel"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Paddel")] <- Paddel1_face
Paddel1_face

Paddel2_face <- alldata_F[which(as.character(alldata_F$target) == "Paddel"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Paddel")] <- Paddel2_face
Paddel2_face

Paddel3_face <- alldata_F[which(as.character(alldata_F$target) == "Paddel"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Paddel")] <- Paddel3_face
Paddel3_face

Paddel4_face <- alldata_F[which(as.character(alldata_F$target) == "Paddel"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Paddel")] <- Paddel4_face
Paddel4_face

Paddel5_face <- alldata_F[which(as.character(alldata_F$target) == "Paddel"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Paddel")] <- Paddel5_face
Paddel5_face


#FACE
#Gebiss 
Gebiss1_face <- alldata_F[which(as.character(alldata_F$target) == "Gebiss"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Gebiss")] <- Gebiss1_face
Gebiss1_face

Gebiss2_face <- alldata_F[which(as.character(alldata_F$target) == "Gebiss"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Gebiss")] <- Gebiss2_face
Gebiss2_face

Gebiss3_face <- alldata_F[which(as.character(alldata_F$target) == "Gebiss"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Gebiss")] <- Gebiss3_face
Gebiss3_face

Gebiss4_face <- alldata_F[which(as.character(alldata_F$target) == "Gebiss"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Gebiss")] <- Gebiss4_face
Gebiss4_face

Gebiss5_face <- alldata_F[which(as.character(alldata_F$target) == "Gebiss"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Gebiss")] <- Gebiss5_face
Gebiss5_face


#FACE
#Feder 
Feder1_face <- alldata_F[which(as.character(alldata_F$target) == "Feder"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Feder")] <- Feder1_face
Feder1_face

Feder2_face <- alldata_F[which(as.character(alldata_F$target) == "Feder"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Feder")] <- Feder2_face
Feder2_face

Feder3_face <- alldata_F[which(as.character(alldata_F$target) == "Feder"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Feder")] <- Feder3_face
Feder3_face

Feder4_face <- alldata_F[which(as.character(alldata_F$target) == "Feder"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Feder")] <- Feder4_face
Feder4_face

Feder5_face <- alldata_F[which(as.character(alldata_F$target) == "Feder"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Feder")] <- Feder5_face
Feder5_face


#FACE
#Schirm 
Schirm1_face <- alldata_F[which(as.character(alldata_F$target) == "Schirm"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Schirm")] <- Schirm1_face
Schirm1_face

Schirm2_face <- alldata_F[which(as.character(alldata_F$target) == "Schirm"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Schirm")] <- Schirm2_face
Schirm2_face

Schirm3_face <- alldata_F[which(as.character(alldata_F$target) == "Schirm"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Schirm")] <- Schirm3_face
Schirm3_face

Schirm4_face <- alldata_F[which(as.character(alldata_F$target) == "Schirm"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Schirm")] <- Schirm4_face
Schirm4_face

Schirm5_face <- alldata_F[which(as.character(alldata_F$target) == "Schirm"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Schirm")] <- Schirm5_face
Schirm5_face


#FACE
#Radio 
Radio1_face <- alldata_F[which(as.character(alldata_F$target) == "Radio"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Radio")] <- Radio1_face
Radio1_face

Radio2_face <- alldata_F[which(as.character(alldata_F$target) == "Radio"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Radio")] <- Radio2_face
Radio2_face

Radio3_face <- alldata_F[which(as.character(alldata_F$target) == "Radio"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Radio")] <- Radio3_face
Radio3_face

Radio4_face <- alldata_F[which(as.character(alldata_F$target) == "Radio"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Radio")] <- Radio4_face
Radio4_face

Radio5_face <- alldata_F[which(as.character(alldata_F$target) == "Radio"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Radio")] <- Radio5_face
Radio5_face


#FACE
#Axt 
Axt1_face <- alldata_F[which(as.character(alldata_F$target) == "Axt"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Axt")] <- Axt1_face
Axt1_face

Axt2_face <- alldata_F[which(as.character(alldata_F$target) == "Axt"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Axt")] <- Axt2_face
Axt2_face

Axt3_face <- alldata_F[which(as.character(alldata_F$target) == "Axt"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Axt")] <- Axt3_face
Axt3_face

Axt4_face <- alldata_F[which(as.character(alldata_F$target) == "Axt"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Axt")] <- Axt4_face
Axt4_face

Axt5_face <- alldata_F[which(as.character(alldata_F$target) == "Axt"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Axt")] <- Axt5_face
Axt5_face

#FACE
#Butter 
Butter1_face <- alldata_F[which(as.character(alldata_F$target) == "Butter"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Butter")] <- Butter1_face
Butter1_face

Butter2_face <- alldata_F[which(as.character(alldata_F$target) == "Butter"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Butter")] <- Butter2_face
Butter2_face

Butter3_face <- alldata_F[which(as.character(alldata_F$target) == "Butter"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Butter")] <- Butter3_face
Butter3_face

Butter4_face <- alldata_F[which(as.character(alldata_F$target) == "Butter"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Butter")] <- Butter4_face
Butter4_face

Butter5_face <- alldata_F[which(as.character(alldata_F$target) == "Butter"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Butter")] <- Butter5_face
Butter5_face


#FACE
#Rüstung 
Rüstung1_face <- alldata_F[which(as.character(alldata_F$target) == "Rüstung"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Rüstung")] <- Rüstung1_face
Rüstung1_face

Rüstung2_face <- alldata_F[which(as.character(alldata_F$target) == "Rüstung"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Rüstung")] <- Rüstung2_face
Rüstung2_face

Rüstung3_face <- alldata_F[which(as.character(alldata_F$target) == "Rüstung"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Rüstung")] <- Rüstung3_face
Rüstung3_face

Rüstung4_face <- alldata_F[which(as.character(alldata_F$target) == "Rüstung"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Rüstung")] <- Rüstung4_face
Rüstung4_face

Rüstung5_face <- alldata_F[which(as.character(alldata_F$target) == "Rüstung"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Rüstung")] <- Rüstung5_face
Rüstung5_face



#FACE
#Hammer 
Hammer1_face <- alldata_F[which(as.character(alldata_F$target) == "Hammer"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hammer")] <- Hammer1_face
Hammer1_face

Hammer2_face <- alldata_F[which(as.character(alldata_F$target) == "Hammer"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hammer")] <- Hammer2_face
Hammer2_face

Hammer3_face <- alldata_F[which(as.character(alldata_F$target) == "Hammer"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hammer")] <- Hammer3_face
Hammer3_face

Hammer4_face <- alldata_F[which(as.character(alldata_F$target) == "Hammer"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hammer")] <- Hammer4_face
Hammer4_face

Hammer5_face <- alldata_F[which(as.character(alldata_F$target) == "Hammer"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Hammer")] <- Hammer5_face
Hammer5_face


#FACE
#Lehrerin 
Lehrerin1_face <- alldata_F[which(as.character(alldata_F$target) == "Lehrerin"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lehrerin")] <- Lehrerin1_face
Lehrerin1_face

Lehrerin2_face <- alldata_F[which(as.character(alldata_F$target) == "Lehrerin"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lehrerin")] <- Lehrerin2_face
Lehrerin2_face

Lehrerin3_face <- alldata_F[which(as.character(alldata_F$target) == "Lehrerin"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lehrerin")] <- Lehrerin3_face
Lehrerin3_face

Lehrerin4_face <- alldata_F[which(as.character(alldata_F$target) == "Lehrerin"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lehrerin")] <- Lehrerin4_face
Lehrerin4_face

Lehrerin5_face <- alldata_F[which(as.character(alldata_F$target) == "Lehrerin"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Lehrerin")] <- Lehrerin5_face
Lehrerin5_face

#FACE
#Mauer

Mauer1_face <- alldata_F[which(as.character(alldata_F$target) == "Mauer"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Mauer")] <- Mauer1_face
Mauer1_face

Mauer2_face <- alldata_F[which(as.character(alldata_F$target) == "Mauer"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Mauer")] <- Mauer2_face
Mauer2_face

Mauer3_face <- alldata_F[which(as.character(alldata_F$target) == "Mauer"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Mauer")] <- Mauer3_face
Mauer3_face

Mauer4_face <- alldata_F[which(as.character(alldata_F$target) == "Mauer"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Mauer")] <- Mauer4_face
Mauer4_face

Mauer5_face <- alldata_F[which(as.character(alldata_F$target) == "Mauer"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Mauer")] <- Mauer5_face
Mauer5_face

#FACE
#Knochen 
Knochen1_face <- alldata_F[which(as.character(alldata_F$target) == "Knochen"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Knochen")] <- Knochen1_face
Knochen1_face

Knochen2_face <- alldata_F[which(as.character(alldata_F$target) == "Knochen"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Knochen")] <- Knochen2_face
Knochen2_face

Knochen3_face <- alldata_F[which(as.character(alldata_F$target) == "Knochen"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Knochen")] <- Knochen3_face
Knochen3_face

Knochen4_face <- alldata_F[which(as.character(alldata_F$target) == "Knochen"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Knochen")] <- Knochen4_face
Knochen4_face

Knochen5_face <- alldata_F[which(as.character(alldata_F$target) == "Knochen"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Knochen")] <- Knochen5_face
Knochen5_face


#FACE
#Pilz 
Pilz1_face <- alldata_F[which(as.character(alldata_F$target) == "Pilz"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Pilz")] <- Pilz1_face
Pilz1_face

Pilz2_face <- alldata_F[which(as.character(alldata_F$target) == "Pilz"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Pilz")] <- Pilz2_face
Pilz2_face

Pilz3_face <- alldata_F[which(as.character(alldata_F$target) == "Pilz"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Pilz")] <- Pilz3_face
Pilz3_face

Pilz4_face <- alldata_F[which(as.character(alldata_F$target) == "Pilz"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Pilz")] <- Pilz4_face
Pilz4_face

Pilz5_face <- alldata_F[which(as.character(alldata_F$target) == "Pilz"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Pilz")] <- Pilz5_face
Pilz5_face

#FACE
#Brücke 
Brücke1_face <- alldata_F[which(as.character(alldata_F$target) == "Brücke"), c("bas_tcfirst")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brücke")] <- Brücke1_face
Brücke1_face

Brücke2_face <- alldata_F[which(as.character(alldata_F$target) == "Brücke"), c("bas_tcsecond")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brücke")] <- Brücke2_face
Brücke2_face

Brücke3_face <- alldata_F[which(as.character(alldata_F$target) == "Brücke"), c("bas_tcthird")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brücke")] <- Brücke3_face
Brücke3_face

Brücke4_face <- alldata_F[which(as.character(alldata_F$target) == "Brücke"), c("bas_tcfourth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brücke")] <- Brücke4_face
Brücke4_face

Brücke5_face <- alldata_F[which(as.character(alldata_F$target) == "Brücke"), c("bas_tcfifth")]
alldata_F$successfulcues_BAS[which(as.character(alldata_F$target) == "Brücke")] <- Brücke5_face
Brücke5_face

```



#non-face

```{r}
alldata$target<-gsub(" ", "", alldata$target, fixed = TRUE)
alldata_NF<-alldata %>% filter(condition=='non-face')

print(alldata_NF)
#alldata_NF$target<-gsub(" ", "", alldata$target, fixed = TRUE)

#non-face
#English
#nonface
#bulb 
bulb1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bulb"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bulb")] <- bulb1_nonface
bulb1_nonface

bulb2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bulb"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bulb")] <- bulb2_nonface
bulb2_nonface

bulb3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bulb"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bulb")] <- bulb3_nonface
bulb3_nonface

bulb4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bulb"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bulb")] <- bulb4_nonface
bulb4_nonface

bulb5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bulb"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bulb")] <- bulb5_nonface
bulb5_nonface


#nonface
#bank 
bank1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bank"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bank")] <- bank1_nonface
bank1_nonface

bank2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bank"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bank")] <- bank2_nonface
bank2_nonface

bank3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bank"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bank")] <- bank3_nonface
bank3_nonface

bank4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bank"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bank")] <- bank4_nonface
bank4_nonface

bank5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bank"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bank")] <- bank5_nonface
bank5_nonface

#nonface
#brewery 
brewery1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "brewery"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "brewery")] <- brewery1_nonface
brewery1_nonface

brewery2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "brewery"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "brewery")] <- brewery2_nonface
brewery2_nonface

brewery3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "brewery"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "brewery")] <- brewery3_nonface
brewery3_nonface

brewery4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "brewery"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "brewery")] <- brewery4_nonface
brewery4_nonface

brewery5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "brewery"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "brewery")] <- brewery5_nonface
brewery5_nonface



#nonface
#crescent 
crescent1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crescent"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crescent")] <- crescent1_nonface
crescent1_nonface

crescent2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crescent"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crescent")] <- crescent2_nonface
crescent2_nonface

crescent3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crescent"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crescent")] <- crescent3_nonface
crescent3_nonface

crescent4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crescent"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crescent")] <- crescent4_nonface
crescent4_nonface

crescent5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crescent"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crescent")] <- crescent5_nonface
crescent5_nonface


#nonface
#affection 
affection1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "affection"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "affection")] <- affection1_nonface
affection1_nonface

affection2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "affection"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "affection")] <- affection2_nonface
affection2_nonface

affection3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "affection"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "affection")] <- affection3_nonface
affection3_nonface

affection4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "affection"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "affection")] <- affection4_nonface
affection4_nonface

affection5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "affection"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "affection")] <- affection5_nonface
affection5_nonface

#nonface
#sill 
sill1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "sill"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "sill")] <- sill1_nonface
sill1_nonface

sill2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "sill"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "sill")] <- sill2_nonface
sill2_nonface

sill3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "sill"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "sill")] <- sill3_nonface
sill3_nonface

sill4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "sill"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "sill")] <- sill4_nonface
sill4_nonface

sill5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "sill"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "sill")] <- sill5_nonface
sill5_nonface



#nonface
#yolk 
yolk1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "yolk"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "yolk")] <- yolk1_nonface
yolk1_nonface

yolk2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "yolk"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "yolk")] <- yolk2_nonface
yolk2_nonface

yolk3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "yolk"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "yolk")] <- yolk3_nonface
yolk3_nonface

yolk4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "yolk"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "yolk")] <- yolk4_nonface
yolk4_nonface

yolk5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "yolk"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "yolk")] <- yolk5_nonface
yolk5_nonface


#nonface
#loaf 
loaf1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "loaf"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "loaf")] <- loaf1_nonface
loaf1_nonface

loaf2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "loaf"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "loaf")] <- loaf2_nonface
loaf2_nonface

loaf3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "loaf"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "loaf")] <- loaf3_nonface
loaf3_nonface

loaf4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "loaf"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "loaf")] <- loaf4_nonface
loaf4_nonface

loaf5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "loaf"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "loaf")] <- loaf5_nonface
loaf5_nonface


#nonface
#cob 
cob1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cob"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cob")] <- cob1_nonface
cob1_nonface

cob2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cob"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cob")] <- cob2_nonface
cob2_nonface

cob3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cob"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cob")] <- cob3_nonface
cob3_nonface

cob4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cob"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cob")] <- cob4_nonface
cob4_nonface

cob5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cob"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cob")] <- cob5_nonface
cob5_nonface


#nonface
#retina 
retina1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "retina"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "retina")] <- retina1_nonface
retina1_nonface

retina2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "retina"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "retina")] <- retina2_nonface
retina2_nonface

retina3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "retina"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "retina")] <- retina3_nonface
retina3_nonface

retina4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "retina"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "retina")] <- retina4_nonface
retina4_nonface

retina5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "retina"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "retina")] <- retina5_nonface
retina5_nonface


#nonface
#grater 
grater1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "grater"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "grater")] <- grater1_nonface
grater1_nonface

grater2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "grater"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "grater")] <- grater2_nonface
grater2_nonface

grater3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "grater"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "grater")] <- grater3_nonface
grater3_nonface

grater4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "grater"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "grater")] <- grater4_nonface
grater4_nonface

grater5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "grater"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "grater")] <- grater5_nonface
grater5_nonface


#nonface
#steed 
steed1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "steed"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "steed")] <- steed1_nonface
steed1_nonface

steed2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "steed"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "steed")] <- steed2_nonface
steed2_nonface

steed3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "steed"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "steed")] <- steed3_nonface
steed3_nonface

steed4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "steed"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "steed")] <- steed4_nonface
steed4_nonface

steed5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "steed"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "steed")] <- steed5_nonface
steed5_nonface

#nonface
#pepperoni 
pepperoni1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "pepperoni"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "pepperoni")] <- pepperoni1_nonface
pepperoni1_nonface

pepperoni2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "pepperoni"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "pepperoni")] <- pepperoni2_nonface
pepperoni2_nonface

pepperoni3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "pepperoni"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "pepperoni")] <- pepperoni3_nonface
pepperoni3_nonface

pepperoni4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "pepperoni"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "pepperoni")] <- pepperoni4_nonface
pepperoni4_nonface

pepperoni5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "pepperoni"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "pepperoni")] <- pepperoni5_nonface
pepperoni5_nonface


#nonface
#cod 
cod1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cod"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cod")] <- cod1_nonface
cod1_nonface

cod2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cod"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cod")] <- cod2_nonface
cod2_nonface

cod3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cod"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cod")] <- cod3_nonface
cod3_nonface

cod4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cod"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cod")] <- cod4_nonface
cod4_nonface

cod5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "cod"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "cod")] <- cod5_nonface
cod5_nonface



#nonface
#crossword 
crossword1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crossword"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crossword")] <- crossword1_nonface
crossword1_nonface

crossword2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crossword"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crossword")] <- crossword2_nonface
crossword2_nonface

crossword3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crossword"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crossword")] <- crossword3_nonface
crossword3_nonface

crossword4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crossword"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crossword")] <- crossword4_nonface
crossword4_nonface

crossword5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "crossword"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "crossword")] <- crossword5_nonface
crossword5_nonface


#nonface
#blaze 
blaze1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "blaze"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "blaze")] <- blaze1_nonface
blaze1_nonface

blaze2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "blaze"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "blaze")] <- blaze2_nonface
blaze2_nonface

blaze3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "blaze"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "blaze")] <- blaze3_nonface
blaze3_nonface

blaze4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "blaze"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "blaze")] <- blaze4_nonface
blaze4_nonface

blaze5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "blaze"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "blaze")] <- blaze5_nonface
blaze5_nonface

#nonface
#occupation

occupation1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "occupation"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "occupation")] <- occupation1_nonface
occupation1_nonface

occupation2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "occupation"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "occupation")] <- occupation2_nonface
occupation2_nonface

occupation3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "occupation"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "occupation")] <- occupation3_nonface
occupation3_nonface

occupation4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "occupation"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "occupation")] <- occupation4_nonface
occupation4_nonface

occupation5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "occupation"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "occupation")] <- occupation5_nonface
occupation5_nonface

#nonface
#butcher 
butcher1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "butcher"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "butcher")] <- butcher1_nonface
butcher1_nonface

butcher2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "butcher"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "butcher")] <- butcher2_nonface
butcher2_nonface

butcher3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "butcher"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "butcher")] <- butcher3_nonface
butcher3_nonface

butcher4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "butcher"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "butcher")] <- butcher4_nonface
butcher4_nonface

butcher5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "butcher"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "butcher")] <- butcher5_nonface
butcher5_nonface


#nonface
#bouquet 
bouquet1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bouquet"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bouquet")] <- bouquet1_nonface
bouquet1_nonface

bouquet2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bouquet"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bouquet")] <- bouquet2_nonface
bouquet2_nonface

bouquet3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bouquet"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bouquet")] <- bouquet3_nonface
bouquet3_nonface

bouquet4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bouquet"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bouquet")] <- bouquet4_nonface
bouquet4_nonface

bouquet5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "bouquet"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "bouquet")] <- bouquet5_nonface
bouquet5_nonface

#nonface
#acquaintance 
acquaintance1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "acquaintance"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "acquaintance")] <- acquaintance1_nonface
acquaintance1_nonface

acquaintance2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "acquaintance"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "acquaintance")] <- acquaintance2_nonface
acquaintance2_nonface

acquaintance3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "acquaintance"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "acquaintance")] <- acquaintance3_nonface
acquaintance3_nonface

acquaintance4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "acquaintance"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "acquaintance")] <- acquaintance4_nonface
acquaintance4_nonface

acquaintance5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "acquaintance"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "acquaintance")] <- acquaintance5_nonface
acquaintance5_nonface

#German non-nonface
#Krone 
Krone1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Krone"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Krone")] <- Krone1_nonface
Krone1_nonface

Krone2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Krone"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Krone")] <- Krone2_nonface
Krone2_nonface

Krone3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Krone"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Krone")] <- Krone3_nonface
Krone3_nonface

Krone4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Krone"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Krone")] <- Krone4_nonface
Krone4_nonface

Krone5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Krone"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Krone")] <- Krone5_nonface
Krone5_nonface


#nonface
#Hafen 
Hafen1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hafen"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hafen")] <- Hafen1_nonface
Hafen1_nonface

Hafen2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hafen"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hafen")] <- Hafen2_nonface
Hafen2_nonface

Hafen3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hafen"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hafen")] <- Hafen3_nonface
Hafen3_nonface

Hafen4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hafen"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hafen")] <- Hafen4_nonface
Hafen4_nonface

Hafen5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hafen"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hafen")] <- Hafen5_nonface
Hafen5_nonface

#nonface
#Brunnen 
Brunnen1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brunnen"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brunnen")] <- Brunnen1_nonface
Brunnen1_nonface

Brunnen2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brunnen"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brunnen")] <- Brunnen2_nonface
Brunnen2_nonface

Brunnen3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brunnen"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brunnen")] <- Brunnen3_nonface
Brunnen3_nonface

Brunnen4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brunnen"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brunnen")] <- Brunnen4_nonface
Brunnen4_nonface

Brunnen5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brunnen"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brunnen")] <- Brunnen5_nonface
Brunnen5_nonface



#nonface
#Kamm 
Kamm1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Kamm"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Kamm")] <- Kamm1_nonface
Kamm1_nonface

Kamm2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Kamm"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Kamm")] <- Kamm2_nonface
Kamm2_nonface

Kamm3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Kamm"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Kamm")] <- Kamm3_nonface
Kamm3_nonface

Kamm4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Kamm"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Kamm")] <- Kamm4_nonface
Kamm4_nonface

Kamm5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Kamm"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Kamm")] <- Kamm5_nonface
Kamm5_nonface


#nonface
#Dach 
Dach1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Dach"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Dach")] <- Dach1_nonface
Dach1_nonface

Dach2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Dach"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Dach")] <- Dach2_nonface
Dach2_nonface

Dach3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Dach"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Dach")] <- Dach3_nonface
Dach3_nonface

Dach4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Dach"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Dach")] <- Dach4_nonface
Dach4_nonface

Dach5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Dach"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Dach")] <- Dach5_nonface
Dach5_nonface

#nonface
#Lilie 
Lilie1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lilie"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lilie")] <- Lilie1_nonface
Lilie1_nonface

Lilie2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lilie"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lilie")] <- Lilie2_nonface
Lilie2_nonface

Lilie3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lilie"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lilie")] <- Lilie3_nonface
Lilie3_nonface

Lilie4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lilie"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lilie")] <- Lilie4_nonface
Lilie4_nonface

Lilie5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lilie"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lilie")] <- Lilie5_nonface
Lilie5_nonface



#nonface
#Paddel 
Paddel1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Paddel"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Paddel")] <- Paddel1_nonface
Paddel1_nonface

Paddel2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Paddel"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Paddel")] <- Paddel2_nonface
Paddel2_nonface

Paddel3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Paddel"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Paddel")] <- Paddel3_nonface
Paddel3_nonface

Paddel4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Paddel"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Paddel")] <- Paddel4_nonface
Paddel4_nonface

Paddel5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Paddel"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Paddel")] <- Paddel5_nonface
Paddel5_nonface


#nonface
#Gebiss 
Gebiss1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Gebiss"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Gebiss")] <- Gebiss1_nonface
Gebiss1_nonface

Gebiss2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Gebiss"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Gebiss")] <- Gebiss2_nonface
Gebiss2_nonface

Gebiss3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Gebiss"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Gebiss")] <- Gebiss3_nonface
Gebiss3_nonface

Gebiss4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Gebiss"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Gebiss")] <- Gebiss4_nonface
Gebiss4_nonface

Gebiss5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Gebiss"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Gebiss")] <- Gebiss5_nonface
Gebiss5_nonface


#nonface
#Feder 
Feder1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Feder"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Feder")] <- Feder1_nonface
Feder1_nonface

Feder2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Feder"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Feder")] <- Feder2_nonface
Feder2_nonface

Feder3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Feder"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Feder")] <- Feder3_nonface
Feder3_nonface

Feder4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Feder"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Feder")] <- Feder4_nonface
Feder4_nonface

Feder5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Feder"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Feder")] <- Feder5_nonface
Feder5_nonface


#nonface
#Schirm 
Schirm1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Schirm"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Schirm")] <- Schirm1_nonface
Schirm1_nonface

Schirm2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Schirm"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Schirm")] <- Schirm2_nonface
Schirm2_nonface

Schirm3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Schirm"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Schirm")] <- Schirm3_nonface
Schirm3_nonface

Schirm4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Schirm"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Schirm")] <- Schirm4_nonface
Schirm4_nonface

Schirm5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Schirm"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Schirm")] <- Schirm5_nonface
Schirm5_nonface


#nonface
#Radio 
Radio1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Radio"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Radio")] <- Radio1_nonface
Radio1_nonface

Radio2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Radio"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Radio")] <- Radio2_nonface
Radio2_nonface

Radio3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Radio"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Radio")] <- Radio3_nonface
Radio3_nonface

Radio4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Radio"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Radio")] <- Radio4_nonface
Radio4_nonface

Radio5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Radio"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Radio")] <- Radio5_nonface
Radio5_nonface


#nonface
#Axt 
Axt1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Axt"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Axt")] <- Axt1_nonface
Axt1_nonface

Axt2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Axt"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Axt")] <- Axt2_nonface
Axt2_nonface

Axt3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Axt"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Axt")] <- Axt3_nonface
Axt3_nonface

Axt4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Axt"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Axt")] <- Axt4_nonface
Axt4_nonface

Axt5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Axt"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Axt")] <- Axt5_nonface
Axt5_nonface

#nonface
#Butter 
Butter1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Butter"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Butter")] <- Butter1_nonface
Butter1_nonface

Butter2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Butter"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Butter")] <- Butter2_nonface
Butter2_nonface

Butter3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Butter"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Butter")] <- Butter3_nonface
Butter3_nonface

Butter4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Butter"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Butter")] <- Butter4_nonface
Butter4_nonface

Butter5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Butter"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Butter")] <- Butter5_nonface
Butter5_nonface


#nonface
#Rüstung 
Rüstung1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Rüstung"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Rüstung")] <- Rüstung1_nonface
Rüstung1_nonface

Rüstung2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Rüstung"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Rüstung")] <- Rüstung2_nonface
Rüstung2_nonface

Rüstung3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Rüstung"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Rüstung")] <- Rüstung3_nonface
Rüstung3_nonface

Rüstung4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Rüstung"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Rüstung")] <- Rüstung4_nonface
Rüstung4_nonface

Rüstung5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Rüstung"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Rüstung")] <- Rüstung5_nonface
Rüstung5_nonface



#nonface
#Hammer 
Hammer1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hammer"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hammer")] <- Hammer1_nonface
Hammer1_nonface

Hammer2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hammer"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hammer")] <- Hammer2_nonface
Hammer2_nonface

Hammer3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hammer"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hammer")] <- Hammer3_nonface
Hammer3_nonface

Hammer4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hammer"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hammer")] <- Hammer4_nonface
Hammer4_nonface

Hammer5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Hammer"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Hammer")] <- Hammer5_nonface
Hammer5_nonface


#nonface
#Lehrerin 
Lehrerin1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lehrerin"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lehrerin")] <- Lehrerin1_nonface
Lehrerin1_nonface

Lehrerin2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lehrerin"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lehrerin")] <- Lehrerin2_nonface
Lehrerin2_nonface

Lehrerin3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lehrerin"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lehrerin")] <- Lehrerin3_nonface
Lehrerin3_nonface

Lehrerin4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lehrerin"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lehrerin")] <- Lehrerin4_nonface
Lehrerin4_nonface

Lehrerin5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Lehrerin"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Lehrerin")] <- Lehrerin5_nonface
Lehrerin5_nonface

#nonface
#Mauer

Mauer1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Mauer"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Mauer")] <- Mauer1_nonface
Mauer1_nonface

Mauer2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Mauer"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Mauer")] <- Mauer2_nonface
Mauer2_nonface

Mauer3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Mauer"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Mauer")] <- Mauer3_nonface
Mauer3_nonface

Mauer4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Mauer"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Mauer")] <- Mauer4_nonface
Mauer4_nonface

Mauer5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Mauer"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Mauer")] <- Mauer5_nonface
Mauer5_nonface

#nonface
#Knochen 
Knochen1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Knochen"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Knochen")] <- Knochen1_nonface
Knochen1_nonface

Knochen2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Knochen"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Knochen")] <- Knochen2_nonface
Knochen2_nonface

Knochen3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Knochen"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Knochen")] <- Knochen3_nonface
Knochen3_nonface

Knochen4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Knochen"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Knochen")] <- Knochen4_nonface
Knochen4_nonface

Knochen5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Knochen"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Knochen")] <- Knochen5_nonface
Knochen5_nonface


#nonface
#Pilz 
Pilz1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Pilz"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Pilz")] <- Pilz1_nonface
Pilz1_nonface

Pilz2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Pilz"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Pilz")] <- Pilz2_nonface
Pilz2_nonface

Pilz3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Pilz"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Pilz")] <- Pilz3_nonface
Pilz3_nonface

Pilz4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Pilz"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Pilz")] <- Pilz4_nonface
Pilz4_nonface

Pilz5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Pilz"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Pilz")] <- Pilz5_nonface
Pilz5_nonface

#nonface
#Brücke 
Brücke1_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brücke"), c("bas_tcfirst")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brücke")] <- Brücke1_nonface
Brücke1_nonface

Brücke2_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brücke"), c("bas_tcsecond")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brücke")] <- Brücke2_nonface
Brücke2_nonface

Brücke3_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brücke"), c("bas_tcthird")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brücke")] <- Brücke3_nonface
Brücke3_nonface

Brücke4_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brücke"), c("bas_tcfourth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brücke")] <- Brücke4_nonface
Brücke4_nonface

Brücke5_nonface <- alldata_NF[which(as.character(alldata_NF$target) == "Brücke"), c("bas_tcfifth")]
alldata_NF$successfulcues_BAS[which(as.character(alldata_NF$target) == "Brücke")] <- Brücke5_nonface
Brücke5_nonface

```


```{r}

x<-c(
coordination_score_vector_face[1], #try1face
coordination_score_vector_face[2],
coordination_score_vector_face[3],
coordination_score_vector_face[4],
coordination_score_vector_face[5],
coordination_score_vector_face[6],
coordination_score_vector_face[7],
coordination_score_vector_face[8],
coordination_score_vector_face[9],
coordination_score_vector_face[10],
coordination_score_vector_face[11] ,#try1face
coordination_score_vector_face[12],
coordination_score_vector_face[13],
coordination_score_vector_face[14],
coordination_score_vector_face[15],
coordination_score_vector_face[16],
coordination_score_vector_face[17],
coordination_score_vector_face[18],
coordination_score_vector_face[19],
coordination_score_vector_face[20],
coordination_score_vector_face[21],#try1face
coordination_score_vector_face[22],
coordination_score_vector_face[23],
coordination_score_vector_face[24],
coordination_score_vector_face[25],
coordination_score_vector_face[26],
coordination_score_vector_face[27],
coordination_score_vector_face[28],
coordination_score_vector_face[29],
coordination_score_vector_face[30],
coordination_score_vector_face[31],#try1face
coordination_score_vector_face[32],
coordination_score_vector_face[33],
coordination_score_vector_face[34],
coordination_score_vector_face[35],
coordination_score_vector_face[36],
coordination_score_vector_face[37],
coordination_score_vector_face[38],
coordination_score_vector_face[39],
coordination_score_vector_face[40],
  
  
coordination_score_vector_nonface[1], #try1nonface
coordination_score_vector_nonface[2],
coordination_score_vector_nonface[3],
coordination_score_vector_nonface[4],
coordination_score_vector_nonface[5],
coordination_score_vector_nonface[6],
coordination_score_vector_nonface[7],
coordination_score_vector_nonface[8],
coordination_score_vector_nonface[9],
coordination_score_vector_nonface[10],
coordination_score_vector_nonface[11] ,#try1nonface
coordination_score_vector_nonface[12],
coordination_score_vector_nonface[13],
coordination_score_vector_nonface[14],
coordination_score_vector_nonface[15],
coordination_score_vector_nonface[16],
coordination_score_vector_nonface[17],
coordination_score_vector_nonface[18],
coordination_score_vector_nonface[19],
coordination_score_vector_nonface[20],
coordination_score_vector_nonface[21],#try1nonface
coordination_score_vector_nonface[22],
coordination_score_vector_nonface[23],
coordination_score_vector_nonface[24],
coordination_score_vector_nonface[25],
coordination_score_vector_nonface[26],
coordination_score_vector_nonface[27],
coordination_score_vector_nonface[28],
coordination_score_vector_nonface[29],
coordination_score_vector_nonface[30],
coordination_score_vector_nonface[31],#try1nonface
coordination_score_vector_nonface[32],
coordination_score_vector_nonface[33],
coordination_score_vector_nonface[34],
coordination_score_vector_nonface[35],
coordination_score_vector_nonface[36],
coordination_score_vector_nonface[37],
coordination_score_vector_nonface[38],
coordination_score_vector_nonface[39],
coordination_score_vector_nonface[40],



coordination_score_vector_face2[1], #try1face
coordination_score_vector_face2[2],
coordination_score_vector_face2[3],
coordination_score_vector_face2[4],
coordination_score_vector_face2[5],
coordination_score_vector_face2[6],
coordination_score_vector_face2[7],
coordination_score_vector_face2[8],
coordination_score_vector_face2[9],
coordination_score_vector_face2[10],
coordination_score_vector_face2[11] ,#try1face
coordination_score_vector_face2[12],
coordination_score_vector_face2[13],
coordination_score_vector_face2[14],
coordination_score_vector_face2[15],
coordination_score_vector_face2[16],
coordination_score_vector_face2[17],
coordination_score_vector_face2[18],
coordination_score_vector_face2[19],
coordination_score_vector_face2[20],
coordination_score_vector_face2[21],#try1face
coordination_score_vector_face2[22],
coordination_score_vector_face2[23],
coordination_score_vector_face2[24],
coordination_score_vector_face2[25],
coordination_score_vector_face2[26],
coordination_score_vector_face2[27],
coordination_score_vector_face2[28],
coordination_score_vector_face2[29],
coordination_score_vector_face2[30],
coordination_score_vector_face2[31],#try1face
coordination_score_vector_face2[32],
coordination_score_vector_face2[33],
coordination_score_vector_face2[34],
coordination_score_vector_face2[35],
coordination_score_vector_face2[36],
coordination_score_vector_face2[37],
coordination_score_vector_face2[38],
coordination_score_vector_face2[39],
coordination_score_vector_face2[40],

coordination_score_vector_nonface2[1], #try1face
coordination_score_vector_nonface2[2],
coordination_score_vector_nonface2[3],
coordination_score_vector_nonface2[4],
coordination_score_vector_nonface2[5],
coordination_score_vector_nonface2[6],
coordination_score_vector_nonface2[7],
coordination_score_vector_nonface2[8],
coordination_score_vector_nonface2[9],
coordination_score_vector_nonface2[10],
coordination_score_vector_nonface2[11] ,#try1face
coordination_score_vector_nonface2[12],
coordination_score_vector_nonface2[13],
coordination_score_vector_nonface2[14],
coordination_score_vector_nonface2[15],
coordination_score_vector_nonface2[16],
coordination_score_vector_nonface2[17],
coordination_score_vector_nonface2[18],
coordination_score_vector_nonface2[19],
coordination_score_vector_nonface2[20],
coordination_score_vector_nonface2[21],#try1face
coordination_score_vector_nonface2[22],
coordination_score_vector_nonface2[23],
coordination_score_vector_nonface2[24],
coordination_score_vector_nonface2[25],
coordination_score_vector_nonface2[26],
coordination_score_vector_nonface2[27],
coordination_score_vector_nonface2[28],
coordination_score_vector_nonface2[29],
coordination_score_vector_nonface2[30],
coordination_score_vector_nonface2[31],#try1face
coordination_score_vector_nonface2[32],
coordination_score_vector_nonface2[33],
coordination_score_vector_nonface2[34],
coordination_score_vector_nonface2[35],
coordination_score_vector_nonface2[36],
coordination_score_vector_nonface2[37],
coordination_score_vector_nonface2[38],
coordination_score_vector_nonface2[39],
coordination_score_vector_nonface2[40],


coordination_score_vector_face3[1], #try1face
coordination_score_vector_face3[2],
coordination_score_vector_face3[3],
coordination_score_vector_face3[4],
coordination_score_vector_face3[5],
coordination_score_vector_face3[6],
coordination_score_vector_face3[7],
coordination_score_vector_face3[8],
coordination_score_vector_face3[9],
coordination_score_vector_face3[10],
coordination_score_vector_face3[11] ,#try1face
coordination_score_vector_face3[12],
coordination_score_vector_face3[13],
coordination_score_vector_face3[14],
coordination_score_vector_face3[15],
coordination_score_vector_face3[16],
coordination_score_vector_face3[17],
coordination_score_vector_face3[18],
coordination_score_vector_face3[19],
coordination_score_vector_face3[20],
coordination_score_vector_face3[21],#try1face
coordination_score_vector_face3[22],
coordination_score_vector_face3[23],
coordination_score_vector_face3[24],
coordination_score_vector_face3[25],
coordination_score_vector_face3[26],
coordination_score_vector_face3[27],
coordination_score_vector_face3[28],
coordination_score_vector_face3[29],
coordination_score_vector_face3[30],
coordination_score_vector_face3[31],#try1face
coordination_score_vector_face3[32],
coordination_score_vector_face3[33],
coordination_score_vector_face3[34],
coordination_score_vector_face3[35],
coordination_score_vector_face3[36],
coordination_score_vector_face3[37],
coordination_score_vector_face3[38],
coordination_score_vector_face3[39],
coordination_score_vector_face3[40],


coordination_score_vector_nonface3[1], #try1face
coordination_score_vector_nonface3[2],
coordination_score_vector_nonface3[3],
coordination_score_vector_nonface3[4],
coordination_score_vector_nonface3[5],
coordination_score_vector_nonface3[6],
coordination_score_vector_nonface3[7],
coordination_score_vector_nonface3[8],
coordination_score_vector_nonface3[9],
coordination_score_vector_nonface3[10],
coordination_score_vector_nonface3[11] ,#try1face
coordination_score_vector_nonface3[12],
coordination_score_vector_nonface3[13],
coordination_score_vector_nonface3[14],
coordination_score_vector_nonface3[15],
coordination_score_vector_nonface3[16],
coordination_score_vector_nonface3[17],
coordination_score_vector_nonface3[18],
coordination_score_vector_nonface3[19],
coordination_score_vector_nonface3[20],
coordination_score_vector_nonface3[21],#try1face
coordination_score_vector_nonface3[22],
coordination_score_vector_nonface3[23],
coordination_score_vector_nonface3[24],
coordination_score_vector_nonface3[25],
coordination_score_vector_nonface3[26],
coordination_score_vector_nonface3[27],
coordination_score_vector_nonface3[28],
coordination_score_vector_nonface3[29],
coordination_score_vector_nonface3[30],
coordination_score_vector_nonface3[31],#try1face
coordination_score_vector_nonface3[32],
coordination_score_vector_nonface3[33],
coordination_score_vector_nonface3[34],
coordination_score_vector_nonface3[35],
coordination_score_vector_nonface3[36],
coordination_score_vector_nonface3[37],
coordination_score_vector_nonface3[38],
coordination_score_vector_nonface3[39],
coordination_score_vector_nonface3[40],

coordination_score_vector_face4[1], #try1face
coordination_score_vector_face4[2],
coordination_score_vector_face4[3],
coordination_score_vector_face4[4],
coordination_score_vector_face4[5],
coordination_score_vector_face4[6],
coordination_score_vector_face4[7],
coordination_score_vector_face4[8],
coordination_score_vector_face4[9],
coordination_score_vector_face4[10],
coordination_score_vector_face4[11],#try1face
coordination_score_vector_face4[12],
coordination_score_vector_face4[13],
coordination_score_vector_face4[14],
coordination_score_vector_face4[15],
coordination_score_vector_face4[16],
coordination_score_vector_face4[17],
coordination_score_vector_face4[18],
coordination_score_vector_face4[19],
coordination_score_vector_face4[20],
coordination_score_vector_face4[21],#try1face
coordination_score_vector_face4[22],
coordination_score_vector_face4[23],
coordination_score_vector_face4[24],
coordination_score_vector_face4[25],
coordination_score_vector_face4[26],
coordination_score_vector_face4[27],
coordination_score_vector_face4[28],
coordination_score_vector_face4[29],
coordination_score_vector_face4[30],
coordination_score_vector_face4[31],#try1face
coordination_score_vector_face4[32],
coordination_score_vector_face4[33],
coordination_score_vector_face4[34],
coordination_score_vector_face4[35],
coordination_score_vector_face4[36],
coordination_score_vector_face4[37],
coordination_score_vector_face4[38],
coordination_score_vector_face4[39],
coordination_score_vector_face4[40],


coordination_score_vector_nonface4[1], #try1face
coordination_score_vector_nonface4[2],
coordination_score_vector_nonface4[3],
coordination_score_vector_nonface4[4],
coordination_score_vector_nonface4[5],
coordination_score_vector_nonface4[6],
coordination_score_vector_nonface4[7],
coordination_score_vector_nonface4[8],
coordination_score_vector_nonface4[9],
coordination_score_vector_nonface4[10],
coordination_score_vector_nonface4[11] ,#try1face
coordination_score_vector_nonface4[12],
coordination_score_vector_nonface4[13],
coordination_score_vector_nonface4[14],
coordination_score_vector_nonface4[15],
coordination_score_vector_nonface4[16],
coordination_score_vector_nonface4[17],
coordination_score_vector_nonface4[18],
coordination_score_vector_nonface4[19],
coordination_score_vector_nonface4[20],
coordination_score_vector_nonface4[21],#try1face
coordination_score_vector_nonface4[22],
coordination_score_vector_nonface4[23],
coordination_score_vector_nonface4[24],
coordination_score_vector_nonface4[25],
coordination_score_vector_nonface4[26],
coordination_score_vector_nonface4[27],
coordination_score_vector_nonface4[28],
coordination_score_vector_nonface4[29],
coordination_score_vector_nonface4[30],
coordination_score_vector_nonface4[31],#try1face
coordination_score_vector_nonface4[32],
coordination_score_vector_nonface4[33],
coordination_score_vector_nonface4[34],
coordination_score_vector_nonface4[35],
coordination_score_vector_nonface4[36],
coordination_score_vector_nonface4[37],
coordination_score_vector_nonface4[38],
coordination_score_vector_nonface4[39],
coordination_score_vector_nonface4[40],


coordination_score_vector_face5[1], #try1face
coordination_score_vector_face5[2],
coordination_score_vector_face5[3],
coordination_score_vector_face5[4],
coordination_score_vector_face5[5],
coordination_score_vector_face5[6],
coordination_score_vector_face5[7],
coordination_score_vector_face5[8],
coordination_score_vector_face5[9],
coordination_score_vector_face5[10],
coordination_score_vector_face5[11],#try1face
coordination_score_vector_face5[12],
coordination_score_vector_face5[13],
coordination_score_vector_face5[14],
coordination_score_vector_face5[15],
coordination_score_vector_face5[16],
coordination_score_vector_face5[17],
coordination_score_vector_face5[18],
coordination_score_vector_face5[19],
coordination_score_vector_face5[20],
coordination_score_vector_face5[21],#try1face
coordination_score_vector_face5[22],
coordination_score_vector_face5[23],
coordination_score_vector_face5[24],
coordination_score_vector_face5[25],
coordination_score_vector_face5[26],
coordination_score_vector_face5[27],
coordination_score_vector_face5[28],
coordination_score_vector_face5[29],
coordination_score_vector_face5[30],
coordination_score_vector_face5[31],#try1face
coordination_score_vector_face5[32],
coordination_score_vector_face5[33],
coordination_score_vector_face5[34],
coordination_score_vector_face5[35],
coordination_score_vector_face5[36],
coordination_score_vector_face5[37],
coordination_score_vector_face5[38],
coordination_score_vector_face5[39],
coordination_score_vector_face5[40],


coordination_score_vector_nonface5[1], #try1face
coordination_score_vector_nonface5[2],
coordination_score_vector_nonface5[3],
coordination_score_vector_nonface5[4],
coordination_score_vector_nonface5[5],
coordination_score_vector_nonface5[6],
coordination_score_vector_nonface5[7],
coordination_score_vector_nonface5[8],
coordination_score_vector_nonface5[9],
coordination_score_vector_nonface5[10],
coordination_score_vector_nonface5[11] ,#try1face
coordination_score_vector_nonface5[12],
coordination_score_vector_nonface5[13],
coordination_score_vector_nonface5[14],
coordination_score_vector_nonface5[15],
coordination_score_vector_nonface5[16],
coordination_score_vector_nonface5[17],
coordination_score_vector_nonface5[18],
coordination_score_vector_nonface5[19],
coordination_score_vector_nonface5[20],
coordination_score_vector_nonface5[21],#try1face
coordination_score_vector_nonface5[22],
coordination_score_vector_nonface5[23],
coordination_score_vector_nonface5[24],
coordination_score_vector_nonface5[25],
coordination_score_vector_nonface5[26],
coordination_score_vector_nonface5[27],
coordination_score_vector_nonface5[28],
coordination_score_vector_nonface5[29],
coordination_score_vector_nonface5[30],
coordination_score_vector_nonface5[31],#try1face
coordination_score_vector_nonface5[32],
coordination_score_vector_nonface5[33],
coordination_score_vector_nonface5[34],
coordination_score_vector_nonface5[35],
coordination_score_vector_nonface5[36],
coordination_score_vector_nonface5[37],
coordination_score_vector_nonface5[38],
coordination_score_vector_nonface5[39],
coordination_score_vector_nonface5[40]

)



y<-c(
median(brewery1_face, na.rm=T),
median(brewery1_face, na.rm=T),
median(sill1_face, na.rm=T),
median(cob1_face, na.rm=T),
median(retina1_face,na.rm=T),
median(loaf1_face,na.rm=T),
median(grater1_face,na.rm=T),
median(yolk1_face,na.rm=T),
median(steed1_face,na.rm=T),
median(cod1_face,na.rm=T),
median(pepperoni1_face,na.rm=T),
median(crossword1_face,nar.rm=T),
median(blaze1_face,nar.rm=T),
median(affection1_face,nar.rm=T),
median(crescent1_face,nar.rm=T),
median(occupation1_face,nar.rm=T),
median(bouquet1_face,nar.rm=T),
median(acquaintance1_face,nar.rm=T),
median(bulb1_face,nar.rm=T),
median(butcher1_face,nar.rm=T),
median(Krone1_face,nar.rm=T),
median(Hafen1_face,nar.rm=T),
median(Brunnen1_face,nar.rm=T),
median(Kamm1_face,nar.rm=T),
median(Dach1_face,nar.rm=T),
median(Lilie1_face,nar.rm=T),
median(Paddel1_face,nar.rm=T),
median(Gebiss1_face,nar.rm=T),
median(Feder1_face,nar.rm=T),
median(Schirm1_face, nar.rm=T),
median(Radio1_face, nar.rm=T),
median(Axt1_face, nar.rm=T),
median(Butter1_face, nar.rm=T),
median(Rüstung1_face, nar.rm=T),
median(Hammer1_face, nar.rm=T),
median(Lehrerin1_face, nar.rm=T),
median(Mauer1_face, nar.rm=T),
median(Knochen1_face, nar.rm=T),
median(Pilz1_face, nar.rm=T),
median(Brücke1_face,nar.rm=T),

median(brewery1_nonface, na.rm=T),
median(brewery1_nonface, na.rm=T),
median(sill1_nonface, na.rm=T),
median(cob1_nonface, na.rm=T),
median(retina1_nonface,na.rm=T),
median(loaf1_nonface,na.rm=T),
median(grater1_nonface,na.rm=T),
median(yolk1_nonface,na.rm=T),
median(steed1_nonface,na.rm=T),
median(cod1_nonface,na.rm=T),
median(pepperoni1_nonface,na.rm=T),
median(crossword1_nonface,nar.rm=T),
median(blaze1_nonface,nar.rm=T),
median(affection1_nonface,nar.rm=T),
median(crescent1_nonface,nar.rm=T),
median(occupation1_nonface,nar.rm=T),
median(bouquet1_nonface,nar.rm=T),
median(acquaintance1_nonface,nar.rm=T),
median(bulb1_nonface,nar.rm=T),
median(butcher1_nonface,nar.rm=T),
median(Krone1_nonface,nar.rm=T),
median(Hafen1_nonface,nar.rm=T),
median(Brunnen1_nonface,nar.rm=T),
median(Kamm1_nonface,nar.rm=T),
median(Dach1_nonface,nar.rm=T),
median(Lilie1_nonface,nar.rm=T),
median(Paddel1_nonface,nar.rm=T),
median(Gebiss1_nonface,nar.rm=T),
median(Feder1_nonface,nar.rm=T),
median(Schirm1_nonface, nar.rm=T),
median(Radio1_nonface, nar.rm=T),
median(Axt1_nonface, nar.rm=T),
median(Butter1_nonface, nar.rm=T),
median(Rüstung1_nonface, nar.rm=T),
median(Hammer1_nonface, nar.rm=T),
median(Lehrerin1_nonface, nar.rm=T),
median(Mauer1_nonface, nar.rm=T),
median(Knochen1_nonface, nar.rm=T),
median(Pilz1_nonface, nar.rm=T),
median(Brücke1_nonface,nar.rm=T),


median(brewery2_face, na.rm=T),
median(brewery2_face, na.rm=T),
median(sill2_face, na.rm=T),
median(cob2_face, na.rm=T),
median(retina2_face,na.rm=T),
median(loaf2_face,na.rm=T),
median(grater2_face,na.rm=T),
median(yolk2_face,na.rm=T),
median(steed2_face,na.rm=T),
median(cod2_face,na.rm=T),
median(pepperoni2_face,na.rm=T),
median(crossword2_face,nar.rm=T),
median(blaze2_face,nar.rm=T),
median(affection2_face,nar.rm=T),
median(crescent2_face,nar.rm=T),
median(occupation2_face,nar.rm=T),
median(bouquet2_face,nar.rm=T),
median(acquaintance2_face,nar.rm=T),
median(bulb2_face,nar.rm=T),
median(butcher2_face,nar.rm=T),
median(Krone2_face,nar.rm=T),
median(Hafen2_face,nar.rm=T),
median(Brunnen2_face,nar.rm=T),
median(Kamm2_face,nar.rm=T),
median(Dach2_face,nar.rm=T),
median(Lilie2_face,nar.rm=T),
median(Paddel2_face,nar.rm=T),
median(Gebiss2_face,nar.rm=T),
median(Feder2_face,nar.rm=T),
median(Schirm2_face, nar.rm=T),
median(Radio2_face, nar.rm=T),
median(Axt2_face, nar.rm=T),
median(Butter2_face, nar.rm=T),
median(Rüstung2_face, nar.rm=T),
median(Hammer2_face, nar.rm=T),
median(Lehrerin2_face, nar.rm=T),
median(Mauer2_face, nar.rm=T),
median(Knochen2_face, nar.rm=T),
median(Pilz2_face, nar.rm=T),
median(Brücke2_face,nar.rm=T),




median(brewery2_nonface, na.rm=T),
median(brewery2_nonface, na.rm=T),
median(sill2_nonface, na.rm=T),
median(cob2_nonface, na.rm=T),
median(retina2_nonface,na.rm=T),
median(loaf2_nonface,na.rm=T),
median(grater2_nonface,na.rm=T),
median(yolk2_nonface,na.rm=T),
median(steed2_nonface,na.rm=T),
median(cod2_nonface,na.rm=T),
median(pepperoni2_nonface,na.rm=T),
median(crossword2_nonface,nar.rm=T),
median(blaze2_nonface,nar.rm=T),
median(affection2_nonface,nar.rm=T),
median(crescent2_nonface,nar.rm=T),
median(occupation2_nonface,nar.rm=T),
median(bouquet2_nonface,nar.rm=T),
median(acquaintance2_nonface,nar.rm=T),
median(bulb2_nonface,nar.rm=T),
median(butcher2_nonface,nar.rm=T),
median(Krone2_nonface,nar.rm=T),
median(Hafen2_nonface,nar.rm=T),
median(Brunnen2_nonface,nar.rm=T),
median(Kamm2_nonface,nar.rm=T),
median(Dach2_nonface,nar.rm=T),
median(Lilie2_nonface,nar.rm=T),
median(Paddel2_nonface,nar.rm=T),
median(Gebiss2_nonface,nar.rm=T),
median(Feder2_nonface,nar.rm=T),
median(Schirm2_nonface, nar.rm=T),
median(Radio2_nonface, nar.rm=T),
median(Axt2_nonface, nar.rm=T),
median(Butter2_nonface, nar.rm=T),
median(Rüstung2_nonface, nar.rm=T),
median(Hammer2_nonface, nar.rm=T),
median(Lehrerin2_nonface, nar.rm=T),
median(Mauer2_nonface, nar.rm=T),
median(Knochen2_nonface, nar.rm=T),
median(Pilz2_nonface, nar.rm=T),
median(Brücke2_nonface,nar.rm=T),


median(brewery3_face, na.rm=T),
median(brewery3_face, na.rm=T),
median(sill3_face, na.rm=T),
median(cob3_face, na.rm=T),
median(retina3_face,na.rm=T),
median(loaf3_face,na.rm=T),
median(grater3_face,na.rm=T),
median(yolk3_face,na.rm=T),
median(steed3_face,na.rm=T),
median(cod3_face,na.rm=T),
median(pepperoni3_face,na.rm=T),
median(crossword3_face,nar.rm=T),
median(blaze3_face,nar.rm=T),
median(affection3_face,nar.rm=T),
median(crescent3_face,nar.rm=T),
median(occupation3_face,nar.rm=T),
median(bouquet3_face,nar.rm=T),
median(acquaintance3_face,nar.rm=T),
median(bulb3_face,nar.rm=T),
median(butcher3_face,nar.rm=T),
median(Krone3_face,nar.rm=T),
median(Hafen3_face,nar.rm=T),
median(Brunnen3_face,nar.rm=T),
median(Kamm3_face,nar.rm=T),
median(Dach3_face,nar.rm=T),
median(Lilie3_face,nar.rm=T),
median(Paddel3_face,nar.rm=T),
median(Gebiss3_face,nar.rm=T),
median(Feder3_face,nar.rm=T),
median(Schirm3_face, nar.rm=T),
median(Radio3_face, nar.rm=T),
median(Axt3_face, nar.rm=T),
median(Butter3_face, nar.rm=T),
median(Rüstung3_face, nar.rm=T),
median(Hammer3_face, nar.rm=T),
median(Lehrerin3_face, nar.rm=T),
median(Mauer3_face, nar.rm=T),
median(Knochen3_face, nar.rm=T),
median(Pilz3_face, nar.rm=T),
median(Brücke3_face,nar.rm=T),


median(brewery3_nonface, na.rm=T),
median(brewery3_nonface, na.rm=T),
median(sill3_nonface, na.rm=T),
median(cob3_nonface, na.rm=T),
median(retina3_nonface,na.rm=T),
median(loaf3_nonface,na.rm=T),
median(grater3_nonface,na.rm=T),
median(yolk3_nonface,na.rm=T),
median(steed3_nonface,na.rm=T),
median(cod3_nonface,na.rm=T),
median(pepperoni3_nonface,na.rm=T),
median(crossword3_nonface,nar.rm=T),
median(blaze3_nonface,nar.rm=T),
median(affection3_nonface,nar.rm=T),
median(crescent3_nonface,nar.rm=T),
median(occupation3_nonface,nar.rm=T),
median(bouquet3_nonface,nar.rm=T),
median(acquaintance3_nonface,nar.rm=T),
median(bulb3_nonface,nar.rm=T),
median(butcher3_nonface,nar.rm=T),
median(Krone3_nonface,nar.rm=T),
median(Hafen3_nonface,nar.rm=T),
median(Brunnen3_nonface,nar.rm=T),
median(Kamm3_nonface,nar.rm=T),
median(Dach3_nonface,nar.rm=T),
median(Lilie3_nonface,nar.rm=T),
median(Paddel3_nonface,nar.rm=T),
median(Gebiss3_nonface,nar.rm=T),
median(Feder3_nonface,nar.rm=T),
median(Schirm3_nonface, nar.rm=T),
median(Radio3_nonface, nar.rm=T),
median(Axt3_nonface, nar.rm=T),
median(Butter3_nonface, nar.rm=T),
median(Rüstung3_nonface, nar.rm=T),
median(Hammer3_nonface, nar.rm=T),
median(Lehrerin3_nonface, nar.rm=T),
median(Mauer3_nonface, nar.rm=T),
median(Knochen3_nonface, nar.rm=T),
median(Pilz3_nonface, nar.rm=T),
median(Brücke3_nonface,nar.rm=T),



median(brewery4_face, na.rm=T),
median(brewery4_face, na.rm=T),
median(sill4_face, na.rm=T),
median(cob4_face, na.rm=T),
median(retina4_face,na.rm=T),
median(loaf4_face,na.rm=T),
median(grater4_face,na.rm=T),
median(yolk4_face,na.rm=T),
median(steed4_face,na.rm=T),
median(cod4_face,na.rm=T),
median(pepperoni4_face,na.rm=T),
median(crossword4_face,nar.rm=T),
median(blaze4_face,nar.rm=T),
median(affection4_face,nar.rm=T),
median(crescent4_face,nar.rm=T),
median(occupation4_face,nar.rm=T),
median(bouquet4_face,nar.rm=T),
median(acquaintance4_face,nar.rm=T),
median(bulb4_face,nar.rm=T),
median(butcher4_face,nar.rm=T),
median(Krone4_face,nar.rm=T),
median(Hafen4_face,nar.rm=T),
median(Brunnen4_face,nar.rm=T),
median(Kamm4_face,nar.rm=T),
median(Dach4_face,nar.rm=T),
median(Lilie4_face,nar.rm=T),
median(Paddel4_face,nar.rm=T),
median(Gebiss4_face,nar.rm=T),
median(Feder4_face,nar.rm=T),
median(Schirm4_face, nar.rm=T),
median(Radio4_face, nar.rm=T),
median(Axt4_face, nar.rm=T),
median(Butter4_face, nar.rm=T),
median(Rüstung4_face, nar.rm=T),
median(Hammer4_face, nar.rm=T),
median(Lehrerin4_face, nar.rm=T),
median(Mauer4_face, nar.rm=T),
median(Knochen4_face, nar.rm=T),
median(Pilz4_face, nar.rm=T),
median(Brücke4_face,nar.rm=T),


median(brewery4_nonface, na.rm=T),
median(brewery4_nonface, na.rm=T),
median(sill4_nonface, na.rm=T),
median(cob4_nonface, na.rm=T),
median(retina4_nonface,na.rm=T),
median(loaf4_nonface,na.rm=T),
median(grater4_nonface,na.rm=T),
median(yolk4_nonface,na.rm=T),
median(steed4_nonface,na.rm=T),
median(cod4_nonface,na.rm=T),
median(pepperoni4_nonface,na.rm=T),
median(crossword4_nonface,nar.rm=T),
median(blaze4_nonface,nar.rm=T),
median(affection4_nonface,nar.rm=T),
median(crescent4_nonface,nar.rm=T),
median(occupation4_nonface,nar.rm=T),
median(bouquet4_nonface,nar.rm=T),
median(acquaintance4_nonface,nar.rm=T),
median(bulb4_nonface,nar.rm=T),
median(butcher4_nonface,nar.rm=T),
median(Krone4_nonface,nar.rm=T),
median(Hafen4_nonface,nar.rm=T),
median(Brunnen4_nonface,nar.rm=T),
median(Kamm4_nonface,nar.rm=T),
median(Dach4_nonface,nar.rm=T),
median(Lilie4_nonface,nar.rm=T),
median(Paddel4_nonface,nar.rm=T),
median(Gebiss4_nonface,nar.rm=T),
median(Feder4_nonface,nar.rm=T),
median(Schirm4_nonface, nar.rm=T),
median(Radio4_nonface, nar.rm=T),
median(Axt4_nonface, nar.rm=T),
median(Butter4_nonface, nar.rm=T),
median(Rüstung4_nonface, nar.rm=T),
median(Hammer4_nonface, nar.rm=T),
median(Lehrerin4_nonface, nar.rm=T),
median(Mauer4_nonface, nar.rm=T),
median(Knochen4_nonface, nar.rm=T),
median(Pilz4_nonface, nar.rm=T),
median(Brücke4_nonface,nar.rm=T),


median(brewery5_face, na.rm=T),
median(brewery5_face, na.rm=T),
median(sill5_face, na.rm=T),
median(cob5_face, na.rm=T),
median(retina5_face,na.rm=T),
median(loaf5_face,na.rm=T),
median(grater5_face,na.rm=T),
median(yolk5_face,na.rm=T),
median(steed5_face,na.rm=T),
median(cod5_face,na.rm=T),
median(pepperoni5_face,na.rm=T),
median(crossword5_face,nar.rm=T),
median(blaze5_face,nar.rm=T),
median(affection5_face,nar.rm=T),
median(crescent5_face,nar.rm=T),
median(occupation5_face,nar.rm=T),
median(bouquet5_face,nar.rm=T),
median(acquaintance5_face,nar.rm=T),
median(bulb5_face,nar.rm=T),
median(butcher5_face,nar.rm=T),
median(Krone5_face,nar.rm=T),
median(Hafen5_face,nar.rm=T),
median(Brunnen5_face,nar.rm=T),
median(Kamm5_face,nar.rm=T),
median(Dach5_face,nar.rm=T),
median(Lilie5_face,nar.rm=T),
median(Paddel5_face,nar.rm=T),
median(Gebiss5_face,nar.rm=T),
median(Feder5_face,nar.rm=T),
median(Schirm5_face, nar.rm=T),
median(Radio5_face, nar.rm=T),
median(Axt5_face, nar.rm=T),
median(Butter5_face, nar.rm=T),
median(Rüstung5_face, nar.rm=T),
median(Hammer5_face, nar.rm=T),
median(Lehrerin5_face, nar.rm=T),
median(Mauer5_face, nar.rm=T),
median(Knochen5_face, nar.rm=T),
median(Pilz5_face, nar.rm=T),
median(Brücke5_face,nar.rm=T),


median(brewery5_nonface, na.rm=T),
median(brewery5_nonface, na.rm=T),
median(sill5_nonface, na.rm=T),
median(cob5_nonface, na.rm=T),
median(retina5_nonface,na.rm=T),
median(loaf5_nonface,na.rm=T),
median(grater5_nonface,na.rm=T),
median(yolk5_nonface,na.rm=T),
median(steed5_nonface,na.rm=T),
median(cod5_nonface,na.rm=T),
median(pepperoni5_nonface,na.rm=T),
median(crossword5_nonface,nar.rm=T),
median(blaze5_nonface,nar.rm=T),
median(affection5_nonface,nar.rm=T),
median(crescent5_nonface,nar.rm=T),
median(occupation5_nonface,nar.rm=T),
median(bouquet5_nonface,nar.rm=T),
median(acquaintance5_nonface,nar.rm=T),
median(bulb5_nonface,nar.rm=T),
median(butcher5_nonface,nar.rm=T),
median(Krone5_nonface,nar.rm=T),
median(Hafen5_nonface,nar.rm=T),
median(Brunnen5_nonface,nar.rm=T),
median(Kamm5_nonface,nar.rm=T),
median(Dach5_nonface,nar.rm=T),
median(Lilie5_nonface,nar.rm=T),
median(Paddel5_nonface,nar.rm=T),
median(Gebiss5_nonface,nar.rm=T),
median(Feder5_nonface,nar.rm=T),
median(Schirm5_nonface, nar.rm=T),
median(Radio5_nonface, nar.rm=T),
median(Axt5_nonface, nar.rm=T),
median(Butter5_nonface, nar.rm=T),
median(Rüstung5_nonface, nar.rm=T),
median(Hammer5_nonface, nar.rm=T),
median(Lehrerin5_nonface, nar.rm=T),
median(Mauer5_nonface, nar.rm=T),
median(Knochen5_nonface, nar.rm=T),
median(Pilz5_nonface, nar.rm=T),
median(Brücke5_nonface,nar.rm=T)

)

```


#now the Pearson correlation
```{r}
#correlation
cor.test(x, y, method=c("pearson"))


table(is.na(x)) #F 360, T 40 #359
table(is.na(y)) #F 23, T 377  #22   #

new<-data.frame(c(x,y))
new2 <- new[!is.na(new$x) == !is.na(new$y)]
new2

#plot
pic<-jpeg(filename = 'corcoordbas.jpg')

std<-sd(!is.na(y))
?geom_ribbon
cor<-ggplot(new2, aes(x,y))+
        #shape=
  xlab("Coordination Success by Item")+
  ylab("Backward AS by Item") +
  ylim(0,1)+
  xlim(0,1)+
theme_classic() +
geom_point()+geom_abline()
cor<- cor+geom_ribbon(aes(ymin=y-std, ymax=y+std), fill="steelblue2", alpha=0.1)

cor + theme(panel.background = element_rect(fill = "white", colour = "black", linetype = "solid"), panel.grid.major = element_line(colour = "grey"))



dev.off()

```


#successful/final cues against language plots with target items in ascending order

```{r}
#Englisch BAS
png(file = 'baseng.png')

alldata_E<-alldata %>% filter(language=='English')


# for each target in non-face condition compute median of successfulcues_BAS
target_to_sort <- as.character(unique(alldata_E$target))
medians_of_successfulcues_BAS_for_target_to_sort <- c()
for (index in (1:length(target_to_sort))){
  current_target <- target_to_sort[index]
  current_successfulcues_BAS <- alldata_E$successfulcues_BAS[which((as.character(alldata_E$target)==current_target) & (as.character(alldata_E$condition)=="non-face"))]
  current_median <- median(current_successfulcues_BAS, na.rm = TRUE)
  medians_of_successfulcues_BAS_for_target_to_sort <- append(medians_of_successfulcues_BAS_for_target_to_sort, current_median)
}
sorted_unique_targets <- target_to_sort[order(medians_of_successfulcues_BAS_for_target_to_sort, decreasing = FALSE)]
alldata_E$target <- factor(alldata_E$target, levels=sorted_unique_targets)

pe<-ggplot(alldata_E, aes(x=target, y=successfulcues_BAS, color=condition))+#+ geom_boxplot()
  xlab("English Target Items")+
  ylab("Final Backward AS")+
  geom_boxplot() + geom_point(position=position_jitterdodge(), alpha=0.4) + theme_classic()
pe<- pe + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
pe
dev.off()


# Eng FAS
png(file = 'faseng.png')

alldata_E<-alldata %>% filter(language=='English')


# for each target in non-face condition compute median of successfulcues_BAS
target_to_sort <- as.character(unique(alldata_E$target))
medians_of_successfulcues_FAS_for_target_to_sort <- c()
for (index in (1:length(target_to_sort))){
  current_target <- target_to_sort[index]
  current_successfulcues_FAS <- alldata_E$successfulcues_FAS[which((as.character(alldata_E$target)==current_target) & (as.character(alldata_E$condition)=="non-face"))]
  current_median <- median(current_successfulcues_FAS, na.rm = TRUE)
  medians_of_successfulcues_FAS_for_target_to_sort <- append(medians_of_successfulcues_FAS_for_target_to_sort, current_median)
}
sorted_unique_targets <- target_to_sort[order(medians_of_successfulcues_FAS_for_target_to_sort, decreasing = FALSE)]
alldata_E$target <- factor(alldata_E$target, levels=sorted_unique_targets)

pe<-ggplot(alldata_E, aes(x=target, y=successfulcues_FAS, color=condition))+#+ geom_boxplot()
  xlab("English Target Items")+
  ylab("Final Forward AS")+
  geom_boxplot() + geom_point(position=position_jitterdodge(), alpha=0.4) + theme_classic()
pe<- pe + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
pe
dev.off()



#Deu BAS
png(file = 'basde.png')

alldata_D<-alldata %>% filter(language=='German')

# correct Brücke and Rüstung
targets_for_correction <- unique(as.character(alldata_D$target))
names(targets_for_correction) <- c(1:length(targets_for_correction))
Rüstung <- targets_for_correction[14]
Brücke <- targets_for_correction[20]
alldata_D$target <- as.character(alldata_D$target)
alldata_D$target[which(alldata_D$target == Rüstung)] <- c("Rüstung")
alldata_D$target[which(alldata_D$target == Brücke)] <- c("Brücke")

# for each target in non-face condition compute median of successfulcues_BAS
target_to_sort <- as.character(unique(alldata_D$target))
medians_of_successfulcues_BAS_for_target_to_sort <- c()
for (index in (1:length(target_to_sort))){
  current_target <- target_to_sort[index]
  current_successfulcues_BAS <- alldata_D$successfulcues_BAS[which((as.character(alldata_D$target)==current_target) & (as.character(alldata_D$condition)=="non-face"))]
  current_median <- median(current_successfulcues_BAS, na.rm = TRUE)
  medians_of_successfulcues_BAS_for_target_to_sort <- append(medians_of_successfulcues_BAS_for_target_to_sort, current_median)
}
sorted_unique_targets <- target_to_sort[order(medians_of_successfulcues_BAS_for_target_to_sort, decreasing = FALSE)]
alldata_D$target <- factor(alldata_D$target, levels=sorted_unique_targets)

pe<-ggplot(alldata_D, aes(x=target, y=successfulcues_BAS, color=condition))+#+ geom_boxplot()
  xlab("German Target Items")+
  ylab("Final Backward AS")+
  geom_boxplot() + geom_point(position=position_jitterdodge(), alpha=0.4) + theme_classic()
pe<- pe + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
pe
dev.off()




#Deu FAS
png(file = 'fasde.png')

alldata_D<-alldata %>% filter(language=='German')

# correct Brücke and Rüstung
targets_for_correction <- unique(as.character(alldata_D$target))
names(targets_for_correction) <- c(1:length(targets_for_correction))
Rüstung <- targets_for_correction[14]
Brücke <- targets_for_correction[20]
alldata_D$target <- as.character(alldata_D$target)
alldata_D$target[which(alldata_D$target == Rüstung)] <- c("Rüstung")
alldata_D$target[which(alldata_D$target == Brücke)] <- c("Brücke")

# for each target in non-face condition compute median of successfulcues_FAS
target_to_sort <- as.character(unique(alldata_D$target))
medians_of_successfulcues_FAS_for_target_to_sort <- c()
for (index in (1:length(target_to_sort))){
  current_target <- target_to_sort[index]
  current_successfulcues_FAS <- alldata_D$successfulcues_FAS[which((as.character(alldata_D$target)==current_target) & (as.character(alldata_D$condition)=="non-face"))]
  current_median <- median(current_successfulcues_FAS, na.rm = TRUE)
  medians_of_successfulcues_FAS_for_target_to_sort <- append(medians_of_successfulcues_FAS_for_target_to_sort, current_median)
}
sorted_unique_targets <- target_to_sort[order(medians_of_successfulcues_FAS_for_target_to_sort, decreasing = FALSE)]
alldata_D$target <- factor(alldata_D$target, levels=sorted_unique_targets)

pe<-ggplot(alldata_D, aes(x=target, y=successfulcues_FAS, color=condition))+#+ geom_boxplot()
  xlab("German Target Items")+
  ylab("Final Forward AS")+
  geom_boxplot() + geom_point(position=position_jitterdodge(), alpha=0.4) + theme_classic()
pe<- pe + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  
pe
dev.off()
```




#data signallers for fas and  bas in each try (not only the final successful one)


data fas and bas for signallers by try

```{r}
#signaller_bas
#alldata[alldata$condition == "face", ] 
data_signaller_bas <- data.frame(y=c(alldata$bas_tcfirst, alldata$bas_tcsecond, alldata$bas_tcthird, alldata$bas_tcfourth, alldata$bas_tcfifth), x= c(
                                      rep("1", length(alldata$bas_tcfirst)), 
                                                                                                                                        rep("2", length(alldata$bas_tcsecond)),
                                                                                                                                        rep("3", length(alldata$bas_tcthird)),
                                                                                                                                        rep("4", length(alldata$bas_tcfourth)),
                                                                                                                                        rep("5", length(alldata$bas_tcfifth))), condition=alldata$condition)
print(data_signaller_bas) 

data_signaller_bas$y


#signaller_fas

data_signaller_fas <- data.frame(y=c(alldata$fas_tcfirst, alldata$fas_tcsecond, alldata$fas_tcthird, alldata$fas_tcfourth, alldata$fas_tcfifth), x= c(
                                    rep("1", length(alldata$fas_tcfirst)), 
                                                                                                                                      rep("2", length(alldata$fas_tcsecond)),
                                                                                                                                      rep("3", length(alldata$fas_tcthird)),
                                                                                                                                      rep("4", length(alldata$fas_tcfourth)),
                                                                                                                                      rep("5", length(alldata$fas_tcfifth))), condition=alldata$condition)


```

#Plots for the AS of each try 
```{r}
#fas
data_signaller_fas
png(filename="p2.png")
p2<-ggplot(data_signaller_fas, aes(x=x, y=y, color=condition)) +
ylab("Forward AS of the Signallers") +
xlab("Number of Tries") +
geom_boxplot()+geom_point(position=position_jitterdodge(), alpha=0.4) +  theme_classic() 
p2
dev.off()


#now BAS
png(filename="p3.png")
p3<-ggplot(data_signaller_bas, aes(x=x, y=y, color=condition)) +
ylab("Backward AS of the Signallers") +
xlab("Number of Tries") +
geom_boxplot()+geom_point(position=position_jitterdodge(), alpha=0.4) +  theme_classic() 
p3
dev.off()
```



****************************************************************************************************************************************************************************************************
****************************************************************************************************************************************************************************************************



#LME MODELS

#Data Analysis: Beta Regression

```{r}
#read in combined German and English data with AS
alldata <- read.csv('alldatawithAS_E&G.csv', sep=",",
                    header=TRUE, 
                    na.strings=c("NA","na"), 
                    stringsAsFactors = TRUE) #unlemmatized

print(alldata)
```


*Explanation of the variable terms* 

"condition" refers to the conditions face vs. non-face and "language" to the conditions English vs. German."target" is the item the signaller received.


#Preparation for Beta GLMM:
*Pull out AS (FAS and BAS) of final successful cue (=DV)*

```{r}
#signallers' FAS of the final successful cues

alldata_first <- alldata[which(as.numeric(alldata$numberoftries) == 1), c("fas_tcfirst")]
alldata$successfulcues_FAS[which(as.numeric(alldata$numberoftries) == 1)] <- alldata_first

alldata_second <- alldata[which(as.numeric(alldata$numberoftries) == 2), c("fas_tcsecond")]
alldata$successfulcues_FAS[which(as.numeric(alldata$numberoftries) == 2)] <- alldata_second

alldata_third <- alldata[which(as.numeric(alldata$numberoftries) == 3), c("fas_tcthird")]
alldata$successfulcues_FAS[which(as.numeric(alldata$numberoftries) == 3)] <- alldata_third

alldata_fourth <- alldata[which(as.numeric(alldata$numberoftries) == 4), c("fas_tcfourth")]
alldata$successfulcues_FAS[which(as.numeric(alldata$numberoftries) == 4)] <- alldata_fourth

alldata_fifth <- alldata[which(as.numeric(alldata$numberoftries) == 5), c("fas_tcfifth")]
alldata$successfulcues_FAS[which(as.numeric(alldata$numberoftries) == 5)] <- alldata_fifth


#signallers' BAS of the final successful cues

alldata_first_bas <- alldata[which(as.numeric(alldata$numberoftries) == 1), c("bas_tcfirst")]
alldata$successfulcues_BAS[which(as.numeric(alldata$numberoftries) == 1)] <- alldata_first_bas

alldata_second_bas <- alldata[which(as.numeric(alldata$numberoftries) == 2), c("bas_tcsecond")]
alldata$successfulcues_BAS[which(as.numeric(alldata$numberoftries) == 2)] <- alldata_second_bas

alldata_third_bas <- alldata[which(as.numeric(alldata$numberoftries) == 3), c("bas_tcthird")]
alldata$successfulcues_BAS[which(as.numeric(alldata$numberoftries) == 3)] <- alldata_third_bas

alldata_fourth_bas <- alldata[which(as.numeric(alldata$numberoftries) == 4), c("bas_tcfourth")]
alldata$successfulcues_BAS[which(as.numeric(alldata$numberoftries) == 4)] <- alldata_fourth_bas

alldata_fifth_bas <- alldata[which(as.numeric(alldata$numberoftries) == 5), c("bas_tcfifth")]
alldata$successfulcues_BAS[which(as.numeric(alldata$numberoftries) == 5)] <- alldata_fifth_bas

```

*Why a Beta regression with logit function?*

Beta regression is used because the dependent variable (DV) is bounded between 0 and 1 - it is a probability. 
###not sure about the link function "logit"!###

*Preliminary thoughts about random effects structure: Which varying intercepts/slopes do I need, if any?*

Information: The expression  "1+"  examines by-participant varying intercepts and varying predictor (here either condition with levels face vs. nonface or the language condition) slopes with slope/intercept correlation. If I didn't want to have a correlation between the intercepts and slopes I could enter (1|pair) + (0 + condition|pair) in my model. However, I will follow Barr's (2013) approach of a maximal random effects structure and only exclude correlation terms or slopes stepwise in case the model fails converging, is overparametized or its fit is bad as indicated by model comparisons.

Although I'm following Barr's (2013) approach, my knowledge and thoughts stated below are mainly based on explanations by Winter (2020).

(1) Participants may differ in face condition effects (face vs. non-face), so I will fit by-pair varying slopes: *(1+condition|pair)*. 

(2) Participants also differ in the language conditions (English vs. German), but they also differ in each round independent of the language condition, so is *(1+language|pair)* really necessary to include? I don't think so, however, the items/stimuli (=targets) are different for each language. So *(1+language|target)* might be important to account for. At the beginning I will include everything, though, also *(1+language|pair)* as suggested by Barr (2013).

(3) Participants received the stimuli in random order, so the items might differ in the face vs. non-face conditions. It might be useful to include *(1+condition|target)*.

(4) Additionally, an item might be unique  and introduce dependencies and thus influence responses to itself even though participants are different (cf. Winter 2020, 243). Therefore, I will also include a varying intercept for item: *(1|item)*.

(5) Same as (4) can be the case for participants - in my case pairs - which is why I also include a random intercept for pair: *(1|pair)*.

(6) It is also worth investigating whether there is a statistical interaction, for example, *(1|language:target)*. 

#The best models
After various model comparisons and considerations of what makes sense to include (e.g. experimental manipulations even if they reduced model fit), these were the best models

```{r}
#BAS

#round -1 so that intercept is not round 0 (because round starts at one)
alldata$round2 <- as.numeric(alldata$round)-1
print(alldata$round2)


#DV=final (successful) FAS of the signallers
model_BAS<- glmmTMB(alldata$successfulcues_BAS ~ language + condition + condition*language+ numberoftries+ round2+ (1|pair) + (1|target), alldata, beta_family(link="logit"))
summary(model_BAS)

#FAS
# DV= final (successful) FAS of the signallers
model_FAS <- glmmTMB(alldata$successfulcues_FAS ~ condition + language + numberoftries*language + numberoftries+(1|pair) +(1|target), alldata, beta_family(link="logit")) 
summary(model_FAS)
```


(Only a few of many model comparisons:)

```{r}
#relevel
alldata$condition<-factor(alldata$condition, level=c('non-face', 'face'))
alldata$language<-factor(alldata$language, level=c('English', 'German'))
```


#FAS
```{r}

model_FAS_1<- glmmTMB(alldata$successfulcues_FAS ~ language + condition*numberoftries + numberoftries + (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_1) #lang English, nb of tries sig


model_FAS_2<- glmmTMB(alldata$successfulcues_FAS ~ language + condition*numberoftries + numberoftries + (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_2) #intercept, lang Ger, nb of tries sig

anova(model_FAS_1, model_FAS_2) 

model_FAS_3 <- glmmTMB(alldata$successfulcues_FAS ~ condition + language + numberoftries*language + numberoftries+(1|pair) +(1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_3) 

model_FAS <- glmmTMB(alldata$successfulcues_FAS ~ condition + language + numberoftries*language + numberoftries+(1|pair) +(1|target), alldata, beta_family(link="logit")) 
summary(model_FAS)

anova(model_FAS_2, model_FAS)

model_FAS_4<- glmmTMB(alldata$successfulcues_FAS ~ language + numberoftries*language + numberoftries+ condition +(1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_4) #incl cond

model_FAS_5<- glmmTMB(alldata$successfulcues_FAS ~ language + condition + numberoftries*language + numberoftries+ (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_5)


anova(model_FAS_3, model_FAS_4)

model_FAS_6<- glmmTMB(alldata$successfulcues_FAS ~ language + condition + language*condition + numberoftries*language + numberoftries+ (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_6)

anova(model_FAS_5, model_FAS_6)


model_FAS_7<- glmmTMB(alldata$successfulcues_FAS ~ language + numberoftries*language + numberoftries*round + numberoftries+ (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_FAS_7)

anova(model_FAS_6, model_FAS_4)
anova(model_FAS_6, model_FAS_5)
anova(model_FAS_6, model_FAS)
anova(model_FAS, model_FAS_4)

```


#BAS
```{r}

model_BAS_1<- glmmTMB(alldata$successfulcues_BAS ~ language + condition*numberoftries + numberoftries + (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_BAS_1) 

#without interaction term

model_BAS_2<- glmmTMB(alldata$successfulcues_BAS ~ language + condition + numberoftries + (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_BAS_2)


model_BAS_3<- glmmTMB(alldata$successfulcues_BAS ~ language + condition + numberoftries + numberoftries*round+ round+ (1|pair) + (1|target), alldata, beta_family(link="logit")) 
summary(model_BAS_3)


anova(model_BAS_1, model_BAS_2)
anova(model_BAS_2, model_BAS_3)



#round2 (round -1)
model_BAS<- glmmTMB(alldata$successfulcues_BAS ~ language + condition + condition*language+ numberoftries + round2+ numberoftries*round2+(1|pair) + (1|target), alldata, beta_family(link="logit"))
summary(model_BAS)

#round
model_BAS_round<- glmmTMB(alldata$successfulcues_BAS ~ language + condition + condition*language+ numberoftries + round+ numberoftries*round+(1|pair) + (1|target), alldata, beta_family(link="logit"))
summary(model_BAS_round)

anova(model_BAS, model_BAS_round)


model_BAS_round2 <- glmmTMB(alldata$successfulcues_BAS ~ language + condition + condition*language+ numberoftries + round+ (1|pair) + (1|target), alldata, beta_family(link="logit"))
summary(model_BAS_round2)

anova(model_BAS, model_BAS_round2)
```


#model with number of tries as DV
```{r}
#Best fit
model <- lmer(numberoftries ~ condition + language + round + (1 | pair) + (1|target), data = alldata, REML = FALSE)
summary(model) 


#some comparisons

model2<-lmer(numberoftries ~  round + language*round + (1 | pair) + (1|target), data = alldata, REML = FALSE)
summary(model2) 

model3 <- lmer(numberoftries ~ condition + language + round + (1 | pair) + (1|target), data = alldata, REML = FALSE)
summary(model3)

model <- lmer(numberoftries ~ condition + language + round + (1 | pair) + (1|target), data = alldata, REML = FALSE)
summary(model) #better fit than model2
anova(model, model3)

```

#correlation
```{r}
cor.test(alldata$round, alldata$numberoftries, method=c("spearman"))
```


#correlation round and nb of tries; and correlation offinal successful cues by nb of tries and rounds
```{r}
#cor.test
cor.test(alldata$round, alldata$numberoftries, method=c("spearman"))

alldata$round <- as.numeric(alldata$round)
alldata$numberoftries <- as.numeric(alldata$numberoftries)

x<-alldata$round
y<-alldata$successfulcues_BAS
x2<-alldata$numberoftries
                            
cor.test(x, y, method = c("spearman")) 
cor.test(x2, y, method = c("spearman")) 


#plots for  rounds and nb of tries

#nb of tries
jpeg(file="corplot1.jpg")

p<-ggplot(alldata, aes(x=numberoftries, y=successfulcues_BAS, color=condition)) + 
geom_point()+
ylab("Backward AS of the Signallers") +
xlab("Number of Tries to Success") +
geom_boxplot() +geom_point() +  geom_rangeframe() + theme_classic()

plot<-p + theme(panel.grid.major = element_line(size = 0.25,  colour = "grey"), legend.title = element_blank())
plot

dev.off()

#rounds

png(filename="corplot2.png")

f<-ggplot(alldata, aes(x=round, y=successfulcues_BAS, color=condition, shape=condition)) +
geom_point() +  geom_smooth(method=lm,  sd=T, aes(fill=condition), alpha=0.3, fullrange=TRUE)+
ylab("Final Backward AS of the Signallers") +
xlab("Rounds") 
f<- f+theme(legend.position=c(0, 0.5))+  
theme_classic()
f

dev.off()

```


